### 2018-06-27 paper/paper_final.tex
paper stuff

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

\cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi
\begin{document}

%%%%%%%%% TITLE
\title{Convolutional Neural Network to Detect Equivalent Questions in Online Forums  \\ DL-IC 2018 Project}

\author{Luca Scannapieco\\
Politecnico di Milano\\
{\tt\small luca.scannapieco@mail.polimi.it}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Nicola Sosio\\
Politecnico di Milano\\
{\tt\small nicola.sosio@mail.polimi.it}
\and
Maria Chiara Zaccardi\\
Politecnico di Milano\\
{\tt\small mariachiara.zaccardi@mail.polimi.it}
}

\maketitle
%\thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}
   The ABSTRACT should be self contained and explain what the paper is about. Usually abstracts are no longer than 300 words. You should state what are the main contributions of your work and tempt the reader to continue to read your paper. A good abstract briefly describes your problem, approach, and key results. This document is based on the CVPR submission template, and it has been adapted to submit a technical report of a project of the Deep Learning and Image Classification course.
\end{abstract}

%%%%%%%%% BODY TEXT
%------------------------------------------------------------------------
\section{Introduction}
Natural Language Processing (NLP) is just one of several fields emerging from Artificial Intelligence. In NLP we want the machine to process and analyze large amount of natural language data to accomplish very interesting tasks (such as Sentiment Analysis, Language Identification and many others). Nowadays, these tasks are plenty and many works on them has been already carried out \footnote{Here is a very interesting repository collecting several NLP tasks along with their main references: \url{https://github.com/Kyubyong/nlp_tasks}}. In this paper, we focus on the task of predicting whether two questions from an online forum are semantically equivalent, i.e. they can be answered by the exact same answer. This can be a very useful tool for Question-Answering community sites as they typically want to keep their database as less redundant as possible, so to make the searches of their users both faster and more effective. Furthermore, they want to keep people from wasting their time answering to questions that have been already solved. \\
The main contribution of this work is \cite{Bogdanova2015Detecting}. In their work, Bogdanova et al. propose a simple Convolutional Neural Network (CNN) to detect semantically equivalent questions. The proposed network first transforms words into \emph{word embeddings} and then applies a convolutional layer which generates question-wide vectors representations. Finally, pairs of questions are scored using a similarity function. The most interesting experimental result is the evaluation of in-domain word embeddings versus the word embeddings generated using all of the English Wikipedia. In particular, they shown that domain-specific word embeddings achieve higher performances. \\
The authors of the paper accurately described the architecture of the network, but no implementation information is provided. Hence, we have thought it could have been quite challenging to replicate this paper as the first deep-learning project of our life. In particular, our efforts focused mainly on three things: 
\begin{itemize}
    \item The training of in-domain word embeddings
    \item The replication of the network architecture presented in the paper
    \item The evaluation of the network using both the word embeddings trained by Google on the English Wikipedia \footnote{\url{http://nlp.stanford.edu/data/glove.6B.zip}} and those trained by us on the same dataset used to train the network
\end{itemize}

%------------------------------------------------------------------------
\section{Related work}
In this section you should discuss published work that relates to your project. This is expected to be full of references, meaning that you have read the existing literature and you know what you are working on very well. This is not just a list or works, but you are supposed to cluster papers that use similar approaches and compare them each other using very short sentences. I strongly suggest to check \cite{steinhardt, lipton} blog posts for some good practices in writing a paper. A quote that I like very much is \emph{``Research is spending 6 hours reading 35 papers, so you can write one sentence containing 2 references''} \cite{twit:ref}. Keep it in mind while you are writing!
%------------------------------------------------------------------------
\section{Proposed approach}
This is the core of your paper, where you describe the details of the proposed method for solving the problem that you set up in the introduction. This is the most important section. It has to be clear why the chosen approach is the right thing to do with respect to the possible alternatives. The explanation of the method has to be readable and understandable and it should not raise obvious questions from the reader.

You can divide the section in paragraphs or subsections that can be useful for the presentation of your method. Usually at this point you may want to place equations, figures and tables to clarify what you are explaining.
%-------------------------------------------------------------------------
\subsection{Mathematics}
Please number all of your sections and displayed equations.  It is
important for readers to be able to refer to any particular equation.  Just
because you didn't refer to it in the text does not mean some future reader
might not need to refer to it.  It is cumbersome to have to use
circumlocutions like ``the equation second from the top of page 3 column
1''. 
%-------------------------------------------------------------------------
\subsection{Footnotes}
Please use footnotes\footnote {This is what a footnote looks like.  It
often distracts the reader from the main flow of the argument.} sparingly.
Indeed, try to avoid footnotes altogether and include necessary peripheral
observations in
the text (within parentheses, if you prefer, as in this sentence).  If you
wish to use a footnote, place it at the bottom of the column on the page on
which it is referenced. Use Times 8-point type, single-spaced.
%-------------------------------------------------------------------------
\subsection{References}
List and number all bibliographical references in 9-point Times,
single-spaced, at the end of your paper. When referenced in the text,
enclose the citation number in square brackets, for
example~\cite{Authors14}.  Where appropriate, include the name(s) of
editors of referenced books.
%-------------------------------------------------------------------------
\subsection{Illustrations, graphs, and photographs}
All graphics should be centered.  Please ensure that any point you wish to
make is resolvable in a printed copy of the paper.  Resize fonts in figures
to match the font in the body text, and choose line widths which render
effectively in print.  Many readers (and reviewers), even of an electronic
copy, will choose to print your paper in order to read it.  You cannot
insist that they do otherwise, and therefore must not assume that they can
zoom in to see tiny details on a graphic.

When placing figures in \LaTeX, it's almost always best to use
\verb+\includegraphics+, and to specify the  figure width as a multiple of
the line width as in the example below
{\small\begin{verbatim}
   \usepackage[dvips]{graphicx} ...
   \includegraphics[width=0.8\linewidth]
                   {myfile.eps}
\end{verbatim}
}

%------------------------------------------------------------------------
\section{Experiments}
In this section you validate your method showing the experiments that you performed. The experiments will vary depending on the project, but you might compare with previously published methods, perform an ablation study to determine the impact of various components of your system, experiment with different hyperparameters or architectural choices, use visualization techniques to gain insight into how your model works, discuss common failure modes of your model, etc. You should include graphs, tables, or other figures to illustrate your experimental results. Divide in subsections or paragraphs to help the reader navigate in your paper.

\paragraph{Datasets.}
Describe the data you are working with for your project. Usually you need to explain what type of data is it, how much data are you working with and if you applied any pre-processing, filtering, or other special treatment to use it. Remember that you have to cite each dataset you used in your project if it has been published from someone else. Instead, if you collected it by yourself you have to describe accurately how you gathered (and labeled) your data.

\paragraph{Experiments setup.}
Here you describe all the architectural choices of your model, the hyper-parameters of your model, \eg optimizer, learning rate, momentum, batch size and if you cross-validate on them.

\paragraph{Results and discussion.}
Discuss your results and compare with other methods. You can also perform an \emph{ablation study} on your model switching on and off some components to understand their contributions.

\section{Conclusion} 
Summarize your key results. What have you learned from the project and suggest future extensions or new applications of your ideas.

\begin{figure}[t]
\begin{center}
\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
\end{center}
   \caption{Example of caption.  It is set in Roman so that mathematics
   (always set in Roman: $B \sin A = A \sin B$) may be included without an
   ugly clash.}
\label{fig:long}
\label{fig:onecol}
\end{figure}

\begin{figure*}
\begin{center}
\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
\end{center}
   \caption{Example of a short caption, which should be centered.}
\label{fig:short}
\end{figure*}

%-------------------------------------------------------------------------
\section*{Acknowledgements}
Here you can thank all the people that have been helpful during the project, but are not coauthors. It is important to add this section only in the final version that you send to the professors and \textbf{NOT in the review version} in order to not compromise the double blind review process. We thank Andrea Romanoni for the insightful comments during the review of the manuscript, and all the old and new Gods who stand beside us when the deadline is dark and full of terrors.

%-------------------------------------------------------------------------
\appendix
\section{Supplementary Material} 
Supplementary material is not counted toward your 4-6 page limit and should be submitted as a separate zip file. Your supplementary material might include:
\begin{itemize}
    \item Source code (if your project proposed an algorithm, or code that is relevant and important for your project.).
    \item Cool videos, interactive visualizations, demos, etc.
\end{itemize}

\paragraph{Examples of things to NOT put in your supplementary material}
\begin{itemize}
    \item The entire PyTorch/TensorFlow Github source code.
    \item Any code that is larger than 10 MB.
    \item Model checkpoints.
    \item A computer virus.
\end{itemize}

\begin{table}
\begin{center}
\begin{tabular}{|l|c|}
\hline
Method & Frobnability \\
\hline\hline
Theirs & Frumpy \\
Yours & Frobbly \\
Ours & Makes one's heart Frob\\
\hline
\end{tabular}
\end{center}
\caption{Results.   Ours is better.}
\end{table}

%-------------------------------------------------------------------------

{\small
\bibliographystyle{ieee}
\bibliography{bib}
}

\end{document}

### 2018-07-02 dlp/tokenizer.py
tokenizer

@@ -9,34 +9,44 @@ from bs4 import BeautifulSoup
 from nltk import word_tokenize
 import re
 import spacy
+from spacy.tokenizer import Tokenizer 
+from spacy.pipeline import Pipe
+from selectolax.parser import HTMLParser
+from lxml import etree
 
 import dlp.util as util
 
-class Tokenizer(object):
+class TokenizerPosts(object):
     
     def __init__(self, df):
         #super(Tokenizer, self).__init__()
-        self.soups=[BeautifulSoup(q, 'html5lib') for q in list(df["Text"])]
+        self.soups=list(df["Text"])
 
     
-    def __replace_links(self, soup):
-        """
-        Replace the links of a single soup with a unique string
-        """
-        for link in soup.find_all('a'):
-            link.string='thistokenisalink'
-        #return soup
+#    def __replace_links(self, soup):
+#        """
+#        Replace the links of a single soup with a unique string
+#        """
+#        for link in soup.find_all('a'):
+#            link.string='thistokenisalink'
+#        #return soup
     
     
     def __replace_code(self, soup):
         """
         Replace the code of a single soup with a unique string
         """
-        for code in soup.find_all('code'):
-            code.string='thistokeniscode'
-        #return soup
+        code=re.compile(util.CODE)
+        return re.sub(code, 'thistokeniscode', soup)
     
-    
+    def __deletenochar(self, soup):
+        """
+        Delete any no char as \n, \t, .. 
+        """
+        nochar = re.compile(util.NOCHAR)
+        return re.sub(nochar, '', soup)
+
+
     def __replace_time(self, soup_text):
         """
         Replace the time format in the text of a single soup with a unique string
@@ -86,29 +96,51 @@ class Tokenizer(object):
     
     
     def __filter_word(self, token):
+        
         token=self.__replace_time(token)
         token=self.__replace_date(token)
         token=self.__replace_version(token)
         token=self.__replace_path(token)
         token=self.__replace_hexadecimal(token)
         token=self.__replace_variable(token)
+
         return token
     
     def __tokenize_single_soup(self, soup):
         """
         Sanitize and tokenize text of a single soup
         """
-        self.__replace_links(soup)
-        self.__replace_code(soup)
-        soup_text=soup.get_text()
[…]

### 2018-07-02 dlp/util.py

@@ -32,3 +32,5 @@ VERSION= r'(\d+\.\d+(.\d+)*)|(\S*\d+\S*)+'
 PATH= r'(~|\w*|.)?(/\S*)+'
 HEXADECIMAL= r'0x[0-9a-fA-F]+'
 VARIABLE= r'([a-zA-Z0-9]*_+[a-zA-Z0-9]*)+'
+CODE= r'<code>.*</code>'
+NOCHAR = r'(\n)+'

### 2018-07-02 main_embeddings.py

@@ -45,7 +45,7 @@ def main():
     [target_test, context_test, labels_test] = word_embedding.generate_samples(data_test)
     
     preprocess_time= time.clock()-start
-    print("TIME TO PREPREOCESS DATA: ", preprocess_time)
+    print("TIME TO PREPROCESS DATA: ", preprocess_time)
     
     print("Training and validating the model...")
     start=time.clock()

### 2018-07-02 prova.py

@@ -1,0 +1,38 @@
+# -*- coding: utf-8 -*-
+
+import pandas as pd
+import numpy as np
+import time
+
+import dlp.util as util
+from dlp.data_loader import XMLDataLoader
+from dlp.data_filter import XMLDataFilter
+from dlp.data_parser import XMLtoPandasParser
+from dlp.non_dup_generator import NonDupGenerator
+from dlp.train_test_val_generation import TrainTestValGenerator
+from dlp.tokenizer import Tokenizer
+from bs4 import BeautifulSoup
+from nltk import word_tokenize
+import re
+import spacy
+from spacy.tokenizer import Tokenizer 
+from selectolax.parser import HTMLParser
+
+xml_loader = XMLDataLoader()
+posts_root = xml_loader.load_posts()
+links_root = xml_loader.load_links()
+
+#filter the useless rows
+xml_filter = XMLDataFilter()
+posts_root = xml_filter.filter_posts(posts_root)
+links_root = xml_filter.filter_links(links_root)
+xml_to_pandas_parser = XMLtoPandasParser()
+posts_df = xml_to_pandas_parser.to_dataframe_posts(posts_root)
+dup_df = xml_to_pandas_parser.to_dataframe_links(links_root)
+
+
+soups = [soup for soup in posts_df['Text']]
+soup_text = [HTMLParser(soup).root.text() for soup in soups]
+nlp= spacy.load("en")
+tokenizer = Tokenizer(nlp.vocab)
+doc = [[t.lemma_ for t in doc] for doc in tokenizer.pipe(soup_text)]

### 2018-07-02 dlp/util.py
added gensim

@@ -24,11 +24,14 @@ DICTIONARY_WIKI_full = "dlp/data/dictionary_wiki_full.json"
 DICTIONARY_WIKI_10000 = "dlp/data/dictionary_wiki_10000.json"
 EMBEDDING_WIKI_10000_200 = "dlp/data/embedding_wiki_10000_200.csv"
 
+DICTIONARY_GENSIM_10000 = "dlp/data/dictionary_gensim_10000.json"
+EMBEDDING_GENSIM_10000_200 = "dlp/data/embedding_gensim_10000_200.csv"
+
 # DEFINITION OF RE
 
 TIME= r'([0-1]?\d|2[0-3])(?::([0-5]?\d))+'
 DATE= r'\d\d(\d\d)?(-|/)\d\d(-|/)\d\d(\d\d)?'
 VERSION= r'(\d+\.\d+(.\d+)*)|(\S*\d+\S*)+'
-PATH= r'(~|\w*|.)?(/\S*)+'
+PATH= r'(~|\w*|.))?(/\S*)+'
 HEXADECIMAL= r'0x[0-9a-fA-F]+'
 VARIABLE= r'([a-zA-Z0-9]*_+[a-zA-Z0-9]*)+'

### 2018-07-02 main_network.py

@@ -84,7 +84,7 @@ def fitness(window_size, clu, batch_size=128, num_epochs=150):
     model = model_builder.buildModel(window_size=window_size,
                          clu=clu)
     model_builder.compileModel(model)
-    log_dir = "./logs/wiki/" + model_builder.log_dir_name(window_size, clu)
+    log_dir = "./logs/gensim2/" + model_builder.log_dir_name(window_size, clu)
     
     tensorboard = TensorBoard(
         log_dir=log_dir,
@@ -128,7 +128,7 @@ def main():
 #    layer_dict = dict([(layer.name, layer) for layer in model.layers])
 #    embeddings = layer_dict['embedding'].get_weights()[0]
 
-    embeddings = np.loadtxt(util.EMBEDDING_WIKI_10000_200)
+    embeddings = np.loadtxt(util.EMBEDDING_GENSIM_10000_200)
     
     #read train, test and validation set
     posts_df= pd.read_csv(util.TOKENIZED_POSTS, index_col=0, converters={"Tokens": lambda x: x.strip("[]").replace("'","").split(", ")})   
@@ -142,7 +142,7 @@ def main():
     print("TRAINING SET...")
     print(train_df.head(5))
     #read the dictionary
-    with open(util.DICTIONARY_WIKI_10000, 'r') as fp:
+    with open(util.DICTIONARY_GENSIM_10000, 'r') as fp:
         dictionary = json.load(fp)
     dictionary = {k.strip("'"): v for k, v in dictionary.items()}
     print(list(dictionary.keys())[:10])
@@ -156,30 +156,60 @@ def main():
     default_parameters = [window_size, clu]
     
     print("Computing q_length...")
+    print(posts_df['Tokens'].iloc[:10].apply(lambda x : len(x)))
     q_length = posts_df['Tokens'].loc[train_df['Post1Id'].tolist() + train_df['Post2Id'].tolist()].apply(lambda x : len(x)).mean()
     q_length = int(round(q_length))
     x_1_train, x_2_train, y_train = build_indexes_dataset(train_df, posts_df, dictionary, q_length)
-    
+
+
     print("Training and validating the model...")
     start=time.clock()
 
     global model_builder
 
-    x_1_train = x_1_train[:15000]
-    x_2_train = x_2_train[:15000]
-    y_train = y_train[:15000]
+    x_1_train = x_1_train[:128]
+    x_2_train = x_2_train[:128]
+    y_train = y_train[:128]
[…]

### 2018-07-03 paper/paper_final.tex
paper

@@
 \begin{abstract}
-   The ABSTRACT should be self contained and explain what the paper is about.
-Usually abstracts are no longer than 300 words.
-You should state what are the main contributions of your work and tempt the reader to continue to read your paper.
-A good abstract briefly describes your problem, approach, and key results.
-This document is based on the CVPR submission template, and it has been adapted to submit a technical report of a project of the Deep Learning and Image Classification course.
+   In the context of online forums, although two questions may seem very different in terms of vocabulary, length and syntax, they may eventually ask the same thing.
+In this work, we try to detect semantically equivalent questions using a simple Convolutional Neural Network (CNN).
+The proposed CNN generates distributed vector representations \cite{mikolov2013distributed} for pairs of questions and score them using a similarity metric.
+We evaluate in-domain \emph{word embeddings} versus the ones trained by Google using all the English Wikipedia \footnote{\url{http://nlp.stanford.edu/data/glove.6B.zip}}: in the former case, the experimental results are very close to the paper \cite{bogdanova2015detecting} we are trying to replicate, while in the latter case they are a bit worse.
+In particular, in-domain word embeddings do not bring any improvement to the performances as they do in the Bogdanova's work.
 \end{abstract}
@@
 In NLP we want the machine to process and analyze large amount of natural language data to accomplish very interesting tasks (such as Sentiment Analysis, Language Identification and many others).
-Nowadays, these tasks are plenty and many works on them has been already carried out \footnote{Here is a very interesting repository collecting several NLP tasks along with their main references: \url{https://github.com/Kyubyong/nlp_tasks}}.
+Nowadays, these tasks are plenty and many works on them has been already carried out \footnote{Here is a very interesting repository collecting several NLP tasks along with their main references: \\ \url{https://github.com/Kyubyong/nlp_tasks}}.
 In this paper, we focus on the task of predicting whether two questions from an online forum are semantically equivalent, i.e.
 they can be answered by the exact same answer.
-This can be a very useful tool for Question-Answering community sites as they typically want to keep their database as less redundant as possible, so to make the searches of their users both faster and more effective.
-Furthermore, they want to keep people from wasting their time answering to questions that have been already solved.
+This can be a very useful tool for Question-Answering community sites as they typically want to keep their databases as less redundant as possible, so to make the searches of their users both faster and more effective.
+Furthermore, they want to keep people from wasting their time in answering already solved questions.
 \\
-The main contribution of this work is \cite{Bogdanova2015Detecting}.
+The main contribution of this work is \cite{bogdanova2015detecting}.
 In their work, Bogdanova et al.
@@
 \\
-The authors of the paper accurately described the architecture of the network, but no implementation information is provided.
-Hence, we have thought it could have been quite challenging to replicate this paper as the first deep-learning project of our life.
-In particular, our efforts focused mainly on three things:
-\begin{itemize}
-    \item The training of in-domain word embeddings
-    \item The replication of the network architecture presented in the paper
-    \item The evaluation of the network using both the word embeddings trained by Google on the English Wikipedia \footnote{\url{http://nlp.stanford.edu/data/glove.6B.zip}} and those trained by us on the same dataset used to train the network
-\end{itemize}
+In general, the results obtained by our implementation are very close to the ones of the replicated paper.
+The only shortcoming was that the in-domain word embeddings trained by us did not improve the performances as they did in Bogdnova et al.'s work.
+We think this is due to the fact that, since the paper does not provide any description of the model employed to train the domain-specific word-embedddings, it is very likely that our model is significantly different from the one they used.\\
+The authors of the paper accurately described the architecture of the network, but many crucial details of the model are missing in their description.
+Hence, we have found quite stimulating to replicate this paper filling the holes with our own ideas.
+In particular, our efforts focused mainly on the following three aspects that were not explicitly treated in the paper:
+    \paragraph{Handling questions of different sizes.}
+    Bogdanova et al.
+explicitly state that the different sizes of questions is one of the main challenges of their work.
+Nevertheless, they do not specify the way they solved this issue.
+We, therefore, tried to experiment two different solutions: fixing the length of each question to the \textbf{maximum} and the \textbf{mean} length of the questions.The second approach resulted to yield the greater accuracy.
+    \paragraph{The type of convolution.}
+    For the implementation of our network we used a 1-dimensional convolution.
+Indeed, text can be seen as images with the input maps having only one dimension (height, without width) corresponding to the question length and where the number of input maps is nothing but the size of the word embeddings.
+The type of convolution represents another missing detail of \cite{bogdanova2015detecting}.
+    \paragraph{The training of in-domain word embeddings.}
+    The paper does not provide any information about the model used to train in-domain word embeddings.
+Therefore, we based our work on a very good tutorial \footnote{\url{http://adventuresinmachinelearning.com/word2vec-keras-tutorial/}} on how to build a the \emph{word2vec} model \cite{mikolov2013distributed} in Keras.
+However, the experimental results concerning this aspect of our work were not very satisfactory.
 
@@
 \section{Related work}
-In this section you should discuss published work that relates to your project.
-This is expected to be full of references, meaning that you have read the existing literature and you know what you are working on very well.
-This is not just a list or works, but you are supposed to cluster papers that use similar approaches and compare them each other using very short sentences.
-I strongly suggest to check \cite{steinhardt, lipton} blog posts for some good practices in writing a paper.
-A quote that I like very much is \emph{``Research is spending 6 hours reading 35 papers, so you can write one sentence containing 2 references''} \cite{twit:ref}.
-Keep it in mind while you are writing!
+Detecting text similarities is a problem which was probably born before deep learning.
+In \cite{gomaa2013survey}, Gomaa et al.
+survey existing algorithms for both lexical and semantical text similarity.
+All these algorithms have nothing to do with Neural Networks, and can therefore be used as baselines to understand how much deep learning has improved the state-of-the-art.\\
+In \cite{kim2014convolutional}, Kim proposes a very simple CNN architecture trained on top of pre-trained word vectors.
+He experimented the same network on 7 different sentence-level classification tasks and, for each task, he compared the obtained results with the state-of-the-art: the CNN approach improved upon the state-of-the-art on 4 out of 7 tasks.
+Moreover, he proposes a slight modification of the network with 2 channels of word vectors: one that is kept static during the training and one that is fine-tuned via backpropagation.
+Although not explicitly stated, we think this has been the main contribution of \cite{bogdanova2015detecting} as the network architecture is pretty much the same.
+The Kim's architecture represents the state-of-the-art on many NLP sentence classification tasks and it is often used as a layer of more complex networks which need to compute sentence-level distributed vectors representation.
+For example, in \cite{severyn2015learning}, the network is used as a fundamental preprocessing step in a learning-to-rank algorithm.
+\\
+A different but still interesting approach to the problem of text classification, is described in \cite{zhang2015character}.
+In this article, the authors explore treating text as a kind of raw signal at character level, and applying temporal (one-dimensional) Convolutional Network to it.\\
+Different CNN architectures are used for solving a wide range of NLP tasks and many encouraging results have been already achieved.
+Yih et al.
+\cite{yih2014semantic} introduced a novel semantic similarity model based on a CNN architecture for the task of answering single-relation factual questions.
+Hu et al.
+\cite{hu2014convolutional} proposed a CNN architecture for hierarchical sentence modeling and sentence matching.
+Convolution has been also used by Dos Santos et al.
+\cite{dos2014deep} for sentiment analysis of short texts that jointly uses character-level, word-level and sentence-level information.\\
+To tackle the problem of sentences with different lengths, Socher et al.
+\cite{socher2011dynamic}, introduce a novel dynamic pooling layer which computes a fixed-sized representation from the variable-sized matrices.
+Another approach could be to use Long Short-Term Memory (LSTM), generating fixed-sized states from the input sentences (as done in \cite{tai2015improved}).\\
+In \cite{zhou2015c}, a novel model called C-LSTM is presented: this model stack CNN and LSTM in a unified architecture for semantic sentence modeling.
+In this way, they are able to combine the strengths of both architectures.
+In particular, they apply CNN to text data and feed consecutive window features directly to LSTM.
+In this way, their architecture enables LSTM to learn long-range dependencies from higher-order sequential features.
 %------------------------------------------------------------------------
 \section{Proposed approach}
-This is the core of your paper, where you describe the details of the proposed method for solving the problem that you set up in the introduction.
-This is the most important section.
-It has to be clear why the chosen approach is the right thing to do with respect to the possible alternatives.
-The explanation of the method has to be readable and understandable and it should not raise obvious questions from the reader.
+In this section we present our strategy for detecting semantically equivalent questions.
+In subsection 3.1, we describe in detail the architecture of the Neural Network.
+Then, in subsequent subsections, we focus on the decisions we have made about the things left unspecified by Bogdanova et al.
+%-------------------------------------------------------------------------
+\subsection{Neural Network Architecture}
+As detailed in Figure \ref{fig:network}, the input for the network is tokenized text strings of the two questions.
+In the first step, the CNN transforms words into real valued feature vectors, also known as \emph{word embeddings}.
+Next, a convolutional layer is used to construct two distributed vector representations $\vec{r}_{q1}$ and $\vec{r}_{q2}$, one for each input question.
+Finally, the CNN computes a similarity score between $\vec{r}_{q1}$ and $\vec{r}_{q2}$.
+Pairs of questions with similarity above a threshold are considered duplicates.
+Each of these step is explained in more details in the following.
+\begin{figure}[t]
+\begin{center}
+%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
+\includegraphics[width=0.8\linewidth]{img/network.png}
+\end{center}
+\caption{The network architecture.}
+\label{fig:network}
+%\label{fig:onecol}
+\end{figure}
 
-You can divide the section in paragraphs or subsections that can be useful for the presentation of your method.
-Usually at this point you may want to place equations, figures and tables to clarify what you are explaining.
+\subsubsection{From text to embeddings}
+The first layer of the network transforms words into representations that capture syntactic and semantic information about the words.
+The initialization of this layer requires two strictly correlated objects:
+\begin{itemize}
+\item \textbf{The vocabulary}: a dictionary $V$ associating each word of the corpora used to train the embeddings to an integer index.
+In this vocabulary, we must also reserve an index for all the words which are not present in the vocabulary.
+Best practices suggest to have the index $0$ for the \emph{unknown} words and then having the other indexes ordered by most common words.
+\item \textbf{The pre-trained word-embeddings}: a matrix $W_0 \in \mathbb{R}^{|V| \times d}$ where $d$ is the size the word embeddings.
+In this matrix, the $i$-th row corresponds to the word embedding of the $i$-th word in the vocabulary.
+\end{itemize}•
+The input of this layer is a 1-dimensional vector $\vec{q}=[w_1, w_2, ...
+, w_N]$ where the element $w_i$ is an integer number corresponding to the index of the $i$-th word of the question.
+We initialize the layer with our pre-trained word embeddings \footnote{either the word embeddings trained by us or the those trained by Google}, which is the matrix $W_0$.
+This layer, for each index $w_i$ of the input vector, retrieves the corresponding vector representation $\vec{r}^{w_i}$ in matrix $W_0$.
+Hence, the output is a matrix $X_0 \in \mathbb{R}^{N \times d}$.\\
+Notice that if we use pre-trained word embeddings, the values of both the $d$ and $|V|$ have been already decided.
+These two hyper-parameters should have been tuned by people who trained the matrix $W_0$.
+Therefore, we will discuss them later when we will describe the training of in-domain word embeddings.
+Even the question length $N$ is something that will be treated later on.
+
+\subsubsection{The convolution}
+We use a convolutional layer to compute the question-wide distributed vector representations $\vec{r}_{q1}$ and $\vec{r}_{q2}$.
+For each question, the convolutional layer first produces local features around each word in the question.
+Then, it combines these local features using a sum operation to create a fixed-sized feature vector (representation) for the question.\\
+Given a question $q$, the convolutional layer applies a matrix-vector operation to each window of size $k$ of successive windows in $\vec{q}_{emb} = [\vec{r}^{w_1},\vec{r}^{w_2}, ..., \vec{r}^{w_N}]$.
+Let us define the vector $\vec{z}_n \in \mathbb{R}^{dk}$ as the concatenation of a sequence of $k$ word embeddings, centralized in the $n$-th word:
+\begin{center}
+$\vec{z}_n = [\vec{r}^{w_{n-(k-1)/2}},..., \vec{r}^{w_n}, ...,\vec{r}^{w_{n+(k-1)/2)}}]^T$
+\end{center}•
+The convolutional layer computes the $j$-th element of the vector $\vec{r}_{q1} \in \mathbb{R}^{cl_u}$ as follows: 
+\begin{equation}
+[\vec{r}_{q1}]_j = f \left( \sum_{1<n<N}[f(W^1 z_n + b^1)]_j \right)
+\end{equation}•
+where $W^1 \in \mathbb{R}^{cl_u \times dk}$ is the weight matrix of the convolutional layer and $f$ is the hyperbolic tangent function.
+The same matrix is used to extract local features around each word window of the given question.
+The global fixed-sized feature vector for the question is obtained by using the sum over all word windows.\\
+Matrix $W^1$ and vector $b^1$ are parameters to be learned.
+The number of convolutional units $cl_u$ (which corresponds to the size of the question representation), and the size of the word context window $k$ are hyper-parameters to be tuned.
+
+\subsubsection{Similarity score}
+Given $\vec{r}_{q1}$ and $\vec{r}_{q2}$, i.e.
+the representations for the input pair of questions $(q_1, q_2)$, the last layer of the CNN computes a similarity score between $q_1$ and $q_2$.
+In our experiments we use the cosine similarity, i.e.
+the scalar product of the two normalized vectors:
+\begin{center}
+$s(q_1, q_2) = \frac{\vec{r}_{q1}}{\lVert \vec{r}_{q1} \rVert} \cdot \frac{\vec{r}_{q2}}{\lVert \vec{r}_{q2} \rVert}$
+\end{center}•
+
 %-------------------------------------------------------------------------
-\subsection{Mathematics}
-Please number all of your sections and displayed equations.  It is
-important for readers to be able to refer to any particular equation.  Just
-because you didn't refer to it in the text does not mean some future reader
-might not need to refer to it.  It is cumbersome to have to use
-circumlocutions like ``the equation second from the top of page 3 column
-1''. 
+\subsection{Question of different length}
+As starting point let's understand why unequal text length is a problem in NLP. The basic recipe for processing text in neural models is as follows:
+\begin{itemize}\itemsep0.1pt
+\item Convert text to tokens
+\item Convert tokens to token IDs
+\item Look up embedding vectors for IDs and construct a 2D tensor that are input to subsequent layers.
+\end{itemize}•
+Now, most neural network APIs (such as Keras) are “define-and-run” so we cannot change the dimensions of various matrices and tensors during runtime.
+All the techniques that can be used to tackle this issue force us to introduce new hyper-parameters or work-around in our model which are not fundamental for  the NLP task but are present to only handle unequal text lengths.\\
+We decided to try two of these techniques, which we found out to be the best practices:
+\begin{itemize}
+	\item Fixing the length of all the questions to the \textbf{maximum} length. All the questions that are shorter are padded using the \emph{UNKNOWN} word (index $0$ of the vocabulary).
+	\item Fixing the length of all the questions to the \textbf{mean} length. All the questions that are shorter are padded as in the case above; all the questions that are longer are chopped.
+\end{itemize}
+To keep the architecture of our network as simpler as possible we decided to apply this techniques as a preprocessing phase, without adding any further layer to the network architecture.
+Therefore, our network accepts as input only questions of the same length.\\
+The experimental results show that the \emph{max} approach provides the best performances.
+This is probably due to the fact that the \emph{mean} approach is very likely to drop important semantic information from the sentence.
+It is worth mentioning that, in order for the \emph{max} approach to perform at its best, it can be a good choice dropping the outliers, i.e.
+the questions that are too long with respect to the other observations.
 %-------------------------------------------------------------------------
-\subsection{Footnotes}
-Please use footnotes\footnote {This is what a footnote looks like.  It
-often distracts the reader from the main flow of the argument.} sparingly.
-Indeed, try to avoid footnotes altogether and include necessary peripheral
-observations in
-the text (within parentheses, if you prefer, as in this sentence).  If you
-wish to use a footnote, place it at the bottom of the column on the page on
-which it is referenced. Use Times 8-point type, single-spaced.
+\subsection{Type of convolution}
+
 %-------------------------------------------------------------------------
-\subsection{References}
-List and number all bibliographical references in 9-point Times,
-single-spaced, at the end of your paper. When referenced in the text,
-enclose the citation number in square brackets, for
-example~\cite{Authors14}.  Where appropriate, include the name(s) of
-editors of referenced books.
-%-------------------------------------------------------------------------
-\subsection{Illustrations, graphs, and photographs}
-All graphics should be centered.  Please ensure that any point you wish to
-make is resolvable in a printed copy of the paper.  Resize fonts in figures
-to match the font in the body text, and choose line widths which render
-effectively in print.  Many readers (and reviewers), even of an electronic
-copy, will choose to print your paper in order to read it.  You cannot
-insist that they do otherwise, and therefore must not assume that they can
-zoom in to see tiny details on a graphic.
-
-When placing figures in \LaTeX, it's almost always best to use
-\verb+\includegraphics+, and to specify the  figure width as a multiple of
-the line width as in the example below
-{\small\begin{verbatim}
-   \usepackage[dvips]{graphicx} ...
-   \includegraphics[width=0.8\linewidth]
-                   {myfile.eps}
-\end{verbatim}
-}
+\subsection{In-domain Word Embeddings}
 
@@
 \section{Experiments}
-In this section you validate your method showing the experiments that you performed.
-The experiments will vary depending on the project, but you might compare with previously published methods, perform an ablation study to determine the impact of various components of your system, experiment with different hyperparameters or architectural choices, use visualization techniques to gain insight into how your model works, discuss common failure modes of your model, etc.
-You should include graphs, tables, or other figures to illustrate your experimental results.
-Divide in subsections or paragraphs to help the reader navigate in your paper.
 
 \paragraph{Datasets.}
-Describe the data you are working with for your project.
-Usually you need to explain what type of data is it, how much data are you working with and if you applied any pre-processing, filtering, or other special treatment to use it.
-Remember that you have to cite each dataset you used in your project if it has been published from someone else.
-Instead, if you collected it by yourself you have to describe accurately how you gathered (and labeled) your data.
 
 \paragraph{Experiments setup.}
-Here you describe all the architectural choices of your model, the hyper-parameters of your model, \eg optimizer, learning rate, momentum, batch size and if you cross-validate on them.
 
 \paragraph{Results and discussion.}
-Discuss your results and compare with other methods. You can also perform an \emph{ablation study} on your model switching on and off some components to understand their contributions.
 
 \section{Conclusion}
-Summarize your key results. What have you learned from the project and suggest future extensions or new applications of your ideas.
 
-\begin{figure}[t]
-\begin{center}
-\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
-\end{center}
-   \caption{Example of caption.  It is set in Roman so that mathematics
-   (always set in Roman: $B \sin A = A \sin B$) may be included without an
-   ugly clash.}
-\label{fig:long}
-\label{fig:onecol}
-\end{figure}
-
-\begin{figure*}
-\begin{center}
-\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-\end{center}
-   \caption{Example of a short caption, which should be centered.}
-\label{fig:short}
-\end{figure*}
+%\begin{figure*}[t]
+%\begin{center}
+%\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
+%\end{center}
+%   \caption{Example of a short caption, which should be centered.}
+%\label{fig:short}
+%\end{figure*}
 
@@
 \section*{Acknowledgements}
-Here you can thank all the people that have been helpful during the project, but are not coauthors.
-It is important to add this section only in the final version that you send to the professors and \textbf{NOT in the review version} in order to not compromise the double blind review process.
-We thank Andrea Romanoni for the insightful comments during the review of the manuscript, and all the old and new Gods who stand beside us when the deadline is dark and full of terrors.
 
@@
 \section{Supplementary Material}
-Supplementary material is not counted toward your 4-6 page limit and should be submitted as a separate zip file. Your supplementary material might include:
-\begin{itemize}
-    \item Source code (if your project proposed an algorithm, or code that is relevant and important for your project.).
-    \item Cool videos, interactive visualizations, demos, etc.
-\end{itemize}
 
-\paragraph{Examples of things to NOT put in your supplementary material}
-\begin{itemize}
-    \item The entire PyTorch/TensorFlow Github source code.
-    \item Any code that is larger than 10 MB.
-    \item Model checkpoints.
-    \item A computer virus.
-\end{itemize}
-
-\begin{table}
-\begin{center}
-\begin{tabular}{|l|c|}
-\hline
-Method & Frobnability \\
-\hline\hline
-Theirs & Frumpy \\
-Yours & Frobbly \\
-Ours & Makes one's heart Frob\\
-\hline
-\end{tabular}
-\end{center}
-\caption{Results.   Ours is better.}
-\end{table}
+%\begin{table}[t]
+%\begin{center}
+%\begin{tabular}{|l|c|}
+%\hline
+%Method & Frobnability \\
+%\hline\hline
+%Theirs & Frumpy \\
+%Yours & Frobbly \\
+%Ours & Makes one's heart Frob\\
+%\hline
+%\end{tabular}
+%\end{center}
+%\caption{Results.   Ours is better.}
+%\end{table}
 

### 2018-07-03 dlp/tokenizer.py
modify tokenization

@@ -21,7 +21,7 @@ class TokenizerPosts(object):
     def __init__(self, df):
         #super(Tokenizer, self).__init__()
         self.soups=list(df["Text"])
-
+        #self.soups = df
     
 #    def __replace_links(self, soup):
 #        """
@@ -39,12 +39,22 @@ class TokenizerPosts(object):
         code=re.compile(util.CODE)
         return re.sub(code, 'thistokeniscode', soup)
     
+    def __deletetabulation(self, soup):
+        """
+        Delete any tabulation as \n, \t, .. 
+        """
+        tab = re.compile(util.TAB)
+        return re.sub(tab, '', soup)
+    
     def __deletenochar(self, soup):
         """
-        Delete any no char as \n, \t, .. 
+        Delete any no char as £,$,%,..
         """
-        nochar = re.compile(util.NOCHAR)
-        return re.sub(nochar, '', soup)
+        nochar= re.compile(util.NOCHAR)
+        if nochar.fullmatch(soup)==None:
+            #soup=re.sub(nochar, '', soup)        
+            return soup
+    
 
 
     def __replace_time(self, soup_text):
@@ -52,7 +62,9 @@ class TokenizerPosts(object):
         Replace the time format in the text of a single soup with a unique string
         """
         time=re.compile(util.TIME)
-        return re.sub(time, 'thistokenistime', soup_text)
+        if time.fullmatch(soup_text)!=None:
+            soup_text=re.sub(time, 'thistokenistime', soup_text)        
+        return soup_text
     
     
     def __replace_date(self, soup_text):
@@ -60,7 +72,9 @@ class TokenizerPosts(object):
         Replace the date format in the text of a single soup with a unique string
         """
         date=re.compile(util.DATE)
-        return re.sub(date, 'thistokenisdate', soup_text)
+        if date.fullmatch(soup_text)!=None:
+            soup_text=re.sub(date, 'thistokenisdate', soup_text)        
+        return soup_text
     
     
     def __replace_version(self, soup_text):
@@ -68,7 +82,10 @@ class TokenizerPosts(object):
         Replace the version format in the text of a single soup with a unique string
         """
         version=re.compile(util.VERSION)
-        return re.sub(version, 'thistokenisversion', soup_text)
+        #return re.sub(version, 'thistokenisversion', soup_text)
+        if version.fullmatch(soup_text)!=None:
+            soup_text=re.sub(version, 'thistokenisversion', soup_text)        
+        return soup_text
[…]

### 2018-07-03 dlp/util.py

@@ -29,8 +29,9 @@ EMBEDDING_WIKI_10000_200 = "dlp/data/embedding_wiki_10000_200.csv"
 TIME= r'([0-1]?\d|2[0-3])(?::([0-5]?\d))+'
 DATE= r'\d\d(\d\d)?(-|/)\d\d(-|/)\d\d(\d\d)?'
 VERSION= r'(\d+\.\d+(.\d+)*)|(\S*\d+\S*)+'
-PATH= r'(~|\w*|.)?(/\S*)+'
+PATH= r'(~|\w*|.|https?)?(/\S*)+'
 HEXADECIMAL= r'0x[0-9a-fA-F]+'
 VARIABLE= r'([a-zA-Z0-9]*_+[a-zA-Z0-9]*)+'
 CODE= r'<code>.*</code>'
-NOCHAR = r'(\n)+'
+TAB = r'(\n)+'
+NOCHAR = r'(£|\$|%|&|\^|#|§|@|\<|\>|\\)+'

### 2018-07-03 paper/paper_final.tex
Revert "Merge branch 'master' of https://github.com/Lucascanna/deep-learning"
This reverts commit 04f6954c833d2317383692d0524e31ad34392c2c, reversing
changes made to cef2ebff6cd24ba221b8fcb90ad7830749a7868c.

@@
 In this work, we try to detect semantically equivalent questions using a simple Convolutional Neural Network (CNN).
-The proposed CNN generates distributed vector representations \cite{mikolov2013distributed} for pairs of questions and score them using a similarity metric.
-We evaluate in-domain \emph{word embeddings} versus the ones trained by Google using all the English Wikipedia \footnote{\url{http://nlp.stanford.edu/data/glove.6B.zip}}: in the former case, the experimental results are very close to the paper \cite{bogdanova2015detecting} we are trying to replicate, while in the latter case they are a bit worse.
-In particular, in-domain word embeddings do not bring any improvement to the performances as they do in the Bogdanova's work.
+The proposed CNN generates distributed vector representations for pairs of questions and score them using a similarity metric.
+This work is the replication of \cite{bogdanova2015detecting}: we basically try to perform the same experiments and compare our results with theirs.
+The replication turned to be not straightforward since some crucial implementation details are missing in the Bogdanova et al.'s description.
+Hence, we have found quite stimulating to replicate this paper filling the holes with our own ideas.
+In particular, our efforts focused mainly on the following three aspects that were not explicitly treated in the paper: unequal text length, the type of convolution and the training of in-domain word embeddings.
+The final results we obtained are quite close to the our target; whereas the optimal parameters values of the network are quite different from \cite{bogdanova2015detecting}.
 \end{abstract}
@@
 In general, the results obtained by our implementation are very close to the ones of the replicated paper.
-The only shortcoming was that the in-domain word embeddings trained by us did not improve the performances as they did in Bogdnova et al.'s work.
-We think this is due to the fact that, since the paper does not provide any description of the model employed to train the domain-specific word-embedddings, it is very likely that our model is significantly different from the one they used.\\
+Surprisingly, as we will discuss in Section 4, the main differences in the results are about the optimal hyper-parameter values of the network.\\
 The authors of the paper accurately described the architecture of the network, but many crucial details of the model are missing in their description.
@@
 Nevertheless, they do not specify the way they solved this issue.
-We, therefore, tried to experiment two different solutions: fixing the length of each question to the \textbf{maximum} and the \textbf{mean} length of the questions.The second approach resulted to yield the greater accuracy.
+We, therefore, tried to fix the length of each question to the \textbf{maximum} and to the \textbf{mean} length of all the questions.
+The first approach resulted to yield the greater accuracy.
     \paragraph{The type of convolution.}
@@
     The paper does not provide any information about the model used to train in-domain word embeddings.
-Therefore, we based our work on a very good tutorial \footnote{\url{http://adventuresinmachinelearning.com/word2vec-keras-tutorial/}} on how to build a the \emph{word2vec} model \cite{mikolov2013distributed} in Keras.
-However, the experimental results concerning this aspect of our work were not very satisfactory.
+Initially, we tried to build our own \emph{word2vec} model \cite{mikolov2013distributed} to generate word-embeddings using as training data the same dataset used to train the main network \footnote{To do so we followed this good tutorial: \url{http://adventuresinmachinelearning.com/word2vec-keras-tutorial/}}.
+However, the training of this network turned out to be very slow and resulting embeddings perfomed poorly.
+\\
+    We, then, decided to use Gensim, a very simple library which generates word-embeddings given the training data.
+The resulting embeddings performed very well, allowing the main network to achieve up to 90\% of accuracy on the validation set.
 

### 2018-07-03 dlp/tokenizer.py

@@ -9,62 +9,40 @@ from bs4 import BeautifulSoup
 from nltk import word_tokenize
 import re
 import spacy
-from spacy.tokenizer import Tokenizer 
-from spacy.pipeline import Pipe
-from selectolax.parser import HTMLParser
-from lxml import etree
 
 import dlp.util as util
 
-class TokenizerPosts(object):
+class Tokenizer(object):
     
     def __init__(self, df):
         #super(Tokenizer, self).__init__()
-        self.soups=list(df["Text"])
-        #self.soups = df
+        self.soups=[BeautifulSoup(q, 'html5lib') for q in list(df["Text"])]
+
     
-#    def __replace_links(self, soup):
-#        """
-#        Replace the links of a single soup with a unique string
-#        """
-#        for link in soup.find_all('a'):
-#            link.string='thistokenisalink'
-#        #return soup
+    def __replace_links(self, soup):
+        """
+        Replace the links of a single soup with a unique string
+        """
+        for link in soup.find_all('a'):
+            link.string='thistokenisalink'
+        #return soup
     
     
     def __replace_code(self, soup):
         """
         Replace the code of a single soup with a unique string
         """
-        code=re.compile(util.CODE)
-        return re.sub(code, 'thistokeniscode', soup)
+        for code in soup.find_all('code'):
+            code.string='thistokeniscode'
+        #return soup
     
-    def __deletetabulation(self, soup):
-        """
-        Delete any tabulation as \n, \t, .. 
-        """
-        tab = re.compile(util.TAB)
-        return re.sub(tab, '', soup)
     
-    def __deletenochar(self, soup):
-        """
-        Delete any no char as £,$,%,..
-        """
-        nochar= re.compile(util.NOCHAR)
-        if nochar.fullmatch(soup)==None:
-            #soup=re.sub(nochar, '', soup)        
-            return soup
-    
-
-
     def __replace_time(self, soup_text):
         """
         Replace the time format in the text of a single soup with a unique string
         """
         time=re.compile(util.TIME)
-        if time.fullmatch(soup_text)!=None:
-            soup_text=re.sub(time, 'thistokenistime', soup_text)        
-        return soup_text
+        return re.sub(time, 'thistokenistime', soup_text)
     
     
     def __replace_date(self, soup_text):
@@ -72,9 +50,7 @@ class TokenizerPosts(object):
[…]

### 2018-07-03 dlp/util.py

@@ -35,6 +35,3 @@ VERSION= r'(\d+\.\d+(.\d+)*)|(\S*\d+\S*)+'
 PATH= r'(~|\w*|.))?(/\S*)+'
 HEXADECIMAL= r'0x[0-9a-fA-F]+'
 VARIABLE= r'([a-zA-Z0-9]*_+[a-zA-Z0-9]*)+'
-CODE= r'<code>.*</code>'
-TAB = r'(\n)+'
-NOCHAR = r'(£|\$|%|&|\^|#|§|@|\<|\>|\\)+'

### 2018-07-03 main_dataset_generation.py

@@ -15,7 +15,7 @@ from dlp.data_filter import XMLDataFilter
 from dlp.data_parser import XMLtoPandasParser
 from dlp.non_dup_generator import NonDupGenerator
 from dlp.train_test_val_generation import TrainTestValGenerator
-from dlp.tokenizer import TokenizerPosts
+from dlp.tokenizer import Tokenizer
 
 def drop_inconsistent_links(posts_df, links_df):
     cond1 = pd.isnull(posts_df.loc[links_df['Post1Id'].values]['Tokens'].values)
@@ -24,16 +24,15 @@ def drop_inconsistent_links(posts_df, links_df):
     return links_df[cond]
 
 def main():
-    """
+    
     global posts_df
     global dup_df
     dup_df.columns=['isDuplicate', 'Post1Id', 'Post2Id']
     if type(posts_df.index) == pd.RangeIndex: 
         posts_df.set_index('Id', inplace=True)
-    """
     print("Loading data...")
     start = time.clock()
-    
+    """
     #laod the data as xml objects
     xml_loader = XMLDataLoader()
     posts_root = xml_loader.load_posts()
@@ -48,7 +47,7 @@ def main():
     xml_to_pandas_parser = XMLtoPandasParser()
     posts_df = xml_to_pandas_parser.to_dataframe_posts(posts_root)
     dup_df = xml_to_pandas_parser.to_dataframe_links(links_root)
-    
+    """
     load_time = time.clock() - start
     print("TIME TO LOAD AND PREPROCESS THE DATA: ", load_time)
     
@@ -57,12 +56,8 @@ def main():
     start=time.clock()
     print("Tokenizing text..")
     
-    inizio = time.clock()
-    tokenizer = TokenizerPosts(posts_df)
-    posts_df['Tokens'] = tokenizer.tokenize()
-    fine = time.clock()
-    print('tempo per un post: ', fine-inizio )
-
+    tokenizer = Tokenizer(posts_df)
+    posts_df["Tokens"] = tokenizer.tokenize()
     
     tokenization_time= time.clock() - start
     print("TIME TO TOKENIZE THE TEXT: ", tokenization_time)

### 2018-07-03 main_embeddings.py

@@ -45,7 +45,7 @@ def main():
     [target_test, context_test, labels_test] = word_embedding.generate_samples(data_test)
     
     preprocess_time= time.clock()-start
-    print("TIME TO PREPROCESS DATA: ", preprocess_time)
+    print("TIME TO PREPREOCESS DATA: ", preprocess_time)
     
     print("Training and validating the model...")
     start=time.clock()

### 2018-07-03 prova.py

@@ -1,38 +1,0 @@
-# -*- coding: utf-8 -*-
-
-import pandas as pd
-import numpy as np
-import time
-
-import dlp.util as util
-from dlp.data_loader import XMLDataLoader
-from dlp.data_filter import XMLDataFilter
-from dlp.data_parser import XMLtoPandasParser
-from dlp.non_dup_generator import NonDupGenerator
-from dlp.train_test_val_generation import TrainTestValGenerator
-from dlp.tokenizer import Tokenizer
-from bs4 import BeautifulSoup
-from nltk import word_tokenize
-import re
-import spacy
-from spacy.tokenizer import Tokenizer 
-from selectolax.parser import HTMLParser
-
-xml_loader = XMLDataLoader()
-posts_root = xml_loader.load_posts()
-links_root = xml_loader.load_links()
-
-#filter the useless rows
-xml_filter = XMLDataFilter()
-posts_root = xml_filter.filter_posts(posts_root)
-links_root = xml_filter.filter_links(links_root)
-xml_to_pandas_parser = XMLtoPandasParser()
-posts_df = xml_to_pandas_parser.to_dataframe_posts(posts_root)
-dup_df = xml_to_pandas_parser.to_dataframe_links(links_root)
-
-
-soups = [soup for soup in posts_df['Text']]
-soup_text = [HTMLParser(soup).root.text() for soup in soups]
-nlp= spacy.load("en")
-tokenizer = Tokenizer(nlp.vocab)
-doc = [[t.lemma_ for t in doc] for doc in tokenizer.pipe(soup_text)]

### 2018-07-04 paper/paper_final.tex
paper update

@@
 \usepackage{amssymb}
+\usepackage{svg}
 
@@
 [\vec{r}_{q1}]_j = f \left( \sum_{1<n<N}[f(W^1 z_n + b^1)]_j \right)
+\label{eq:conv}
 \end{equation}•
@@
 \subsection{Type of convolution}
+To implement the convolution described in Section 3.1.2., we decided to use a 1-dimensional convolutional layer.
+The reason behind this choice is that, as images are seen as three input maps (R,G,B) where each map is a 2-dimensional array (matrix) with height and width, similarly text can be seen as $d$ input maps where each map has only one dimension which is the length of the question.
+This interpretation of the 1-dimensional convolution is exemplified in Figure \ref{fig:conv}.\\
+After applying vertically the sum operation to the output of this layer, the resulting vector is exactly the one described by Equation \ref{eq:conv}
 
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=0.8\linewidth]{img/conv1d.jpg}
+\end{center}
+\caption{The 1-dimensional convolution.}
+\label{fig:conv}
+\end{figure}
 %-------------------------------------------------------------------------

### 2018-07-04 paper/paper_final.tex
tokenizer paper

--- 2018-07-03 paper/paper_final.tex
@@
 
+\paragraph{Tokenization.}
+Tokenization is the process of breaking up a given text, in this case every question, into units called tokens.
+The tokens may be words or number or punctuation mark: we decide to consider only words and to disregard those tokens that are punctuation, symbols, tabulation, white spaces, articles and prepositions.
+For each word we took only its lemma.
+Lemmatization is a morphological analysis of words, aiming to remove inflectional forms and to return the base or dictionary form of a word, which is known as the lemma.
+
+Then we noticed that some patterns are very frequent but not so relevant in their different form. Therefore we had some other precautions:
+\begin{itemize}
+	\item html tags that are \texttt{code} tags are replaced by the string \texttt{thistokeniscode}
+	\item html tags that are \texttt{a} tags are replaced by the string \texttt{thistokenislink}
+	\item tokens that match with a time format are replaced by the string \texttt{thistokenistime}
+	\item tokens that match with a date format are replaced by the string \texttt{thistokenisdate}
+	\item tokens that match with a version format are replaced by the string \texttt{thistokenisversion}
+	\item tokens that match with a path format are replaced by the string \texttt{thistokenispath}
+	\item tokens that match with a hexadecimal format are replaced by the string \texttt{thistokenishexadecimal}
+ \end{itemize}
+
 \paragraph{Experiments setup.}

### 2018-07-04 dlp/util.py

@@ -32,7 +32,7 @@ EMBEDDING_GENSIM_10000_200 = "dlp/data/embedding_gensim_10000_200.csv"
 TIME= r'([0-1]?\d|2[0-3])(?::([0-5]?\d))+'
 DATE= r'\d\d(\d\d)?(-|/)\d\d(-|/)\d\d(\d\d)?'
 VERSION= r'(\d+\.\d+(.\d+)*)|(\S*\d+\S*)+'
-PATH= r'(~|\w*|.))?(/\S*)+'
+PATH= r'(~|\w*|.)?(/\S*)+'
 HEXADECIMAL= r'0x[0-9a-fA-F]+'
 VARIABLE= r'([a-zA-Z0-9]*_+[a-zA-Z0-9]*)+'
 CODE= r'<code>.*</code>'

### 2018-07-04 paper/paper_final.tex
Dataset paper

--- 2018-07-04 paper/paper_final.tex
@@
 \\
+
 In general, the results obtained by our implementation are very close to the ones of the replicated paper.
@@
 \subsection{Type of convolution}
+
 To implement the convolution described in Section 3.1.2., we decided to use a 1-dimensional convolutional layer.
@@
 \paragraph{Datasets.}
+Our dataset is from Ask Ubuntu Community Questions and Answers site \footnote{http://askubuntu.com}.
+Ask Ubuntu is a community for Ubuntu users and developers, and it is part of the Stack Exchange Q\&A communities.
+The users of these communities can ask and answer ques- tions, and vote up and down both questions and answers.
+Users with high reputation become moderators and can label a new question as a duplicate to an existing question.
+Usually it takes five votes from different moderators to close a question or to mark it as a duplicate.
+We use Ask Ubuntu data dump \footnote{ \url{https://archive.org/download/stackexchange}} provided in April 2018, that contains posts from 2010 to March 2018.
+From the data dump we have selected only the posts that are questions, the amount of questions is 285651.
+We extract all question pairs linked as duplicated and from those we consider only 15500 pairs in order to be able to compare the obtained results with the ones from the paper \cite{bogdanova2015detecting}.
+Afterward we have randomly generated the same number of non duplicate pair of posts.
+\\
+For our experiments, we divide the dataset in the same way of the paper \cite{bogdanova2015detecting}: 24K pairs for the training set, 6K pairs for the test set and 1K pairs for the validation set.
+
+\paragraph{Tokenization.}
+Tokenization is the process of breaking up a given text, in this case every question, into units called tokens.
+The tokens may be words or number or punctuation mark: we decide to consider only words and to disregard those tokens that are punctuation, symbols, tabulation, white spaces, articles and prepositions.
+For each word we took only its lemma.
+Lemmatization is a morphological analysis of words, aiming to remove inflectional forms and to return the base or dictionary form of a word, which is known as the lemma.
+
+Then we noticed that some patterns are very frequent but not so relevant in their different form. Therefore we had some other precautions:
+\begin{itemize}
+	\item html tags that are \texttt{code} tags are replaced by the string \texttt{thistokeniscode}
+	\item html tags that are \texttt{a} tags are replaced by the string \texttt{thistokenislink}
+	\item tokens that match with a time format are replaced by the string \texttt{thistokenistime}
+	\item tokens that match with a date format are replaced by the string \texttt{thistokenisdate}
+	\item tokens that match with a version format are replaced by the string \texttt{thistokenisversion}
+	\item tokens that match with a path format are replaced by the string \texttt{thistokenispath}
+	\item tokens that match with a hexadecimal format are replaced by the string \texttt{thistokenishexadecimal}
+ \end{itemize}
 

### 2018-07-05 paper/paper_final.tex
paper update

@@
 The final results we obtained are quite close to the our target; whereas the optimal parameters values of the network are quite different from \cite{bogdanova2015detecting}.
+It is worth clarifying that, since we used domain-specific data for both training and testing the model, the obtained performances are guaranteed to hold only for pairs of questions coming from that specific domain.
 \end{abstract}
@@
 Initially, we tried to build our own \emph{word2vec} model \cite{mikolov2013distributed} to generate word-embeddings using as training data the same dataset used to train the main network \footnote{To do so we followed this good tutorial: \url{http://adventuresinmachinelearning.com/word2vec-keras-tutorial/}}.
-However, the training of this network turned out to be very slow and resulting embeddings perfomed poorly.
+However, the training of this network turned out to be very slow and resulting embeddings performed poorly.
 \\
@@
 Best practices suggest to have the index $0$ for the \emph{unknown} words and then having the other indexes ordered by most common words.
-\item \textbf{The pre-trained word-embeddings}: a matrix $W_0 \in \mathbb{R}^{|V| \times d}$ where $d$ is the size the word embeddings.
+\item \textbf{The pre-trained word-embeddings}: a matrix $W_0 \in \mathbb{R}^{|V| \times d}$ where $d$ is the size of the word embeddings.
 In this matrix, the $i$-th row corresponds to the word embedding of the $i$-th word in the vocabulary.
@@
 Hence, the output is a matrix $X_0 \in \mathbb{R}^{N \times d}$.\\
-Notice that if we use pre-trained word embeddings, the values of both the $d$ and $|V|$ have been already decided.
-These two hyper-parameters should have been tuned by people who trained the matrix $W_0$.
-Therefore, we will discuss them later when we will describe the training of in-domain word embeddings.
-Even the question length $N$ is something that will be treated later on.
+Notice that using pre-trained word embeddings, implies that the values of both the $d$ and $|V|$ have been already decided by those who trained the matrix $W_0$.
 
@@
 Given a question $q$, the convolutional layer applies a matrix-vector operation to each window of size $k$ of successive windows in $\vec{q}_{emb} = [\vec{r}^{w_1},\vec{r}^{w_2}, ..., \vec{r}^{w_N}]$.
-Let us define the vector $\vec{z}_n \in \mathbb{R}^{dk}$ as the concatenation of a sequence of $k$ word embeddings, centralized in the $n$-th word:
+Let us define the vector $\vec{z}_n \in \mathbb{R}^{dk}$ as the concatenation of a sequence of $k$ word embeddings, starting from the $n$-th word:
 \begin{center}
-$\vec{z}_n = [\vec{r}^{w_{n-(k-1)/2}},..., \vec{r}^{w_n}, ...,\vec{r}^{w_{n+(k-1)/2)}}]^T$
+$\vec{z}_n = [\vec{r}^{w_n}, ... ,\vec{r}^{w_{n+k-1}}]^T$
 \end{center}•
-The convolutional layer computes the $j$-th element of the vector $\vec{r}_{q1} \in \mathbb{R}^{cl_u}$ as follows: 
+The convolutional layer computes the $j$-th element of the vector $\vec{r}_{q} \in \mathbb{R}^{cl_u}$ as follows: 
 \begin{equation}
-[\vec{r}_{q1}]_j = f \left( \sum_{1<n<N}[f(W^1 z_n + b^1)]_j \right)
+[\vec{r}_{q}]_j = f \left( \sum_{1<n<N-k+1}[f(W^1 z_n + b^1)]_j \right)
 \label{eq:conv}
@@
 \subsection{In-domain Word Embeddings}    
-
+The training of in-domain word embeddings was one of the hardest task of our work. 
 %------------------------------------------------------------------------

### 2018-07-06 plotter.py
plotter

@@ -1,0 +1,80 @@
+import argparse
+import tensorflow as tf
+from tensorboard.backend.event_processing.event_accumulator import EventAccumulator
+from tensorboard.backend.event_processing.event_multiplexer import EventMultiplexer
+
+from matplotlib import pyplot as plt
+from scipy.interpolate import spline
+import numpy as np
+from matplotlib import colors as colors
+import seaborn as sns
+
+plt.switch_backend('agg')
+sns.set(style="darkgrid")
+sns.set_context("paper")
+
+
+def plot(params):
+    ''' beautify tf log
+        Use better library (seaborn) to plot tf event file'''
+
+    log_path = params['logdir']
+    fname = params['filename']
+    title = params['title']
+
+    accs = EventMultiplexer().AddRunsFromDirectory(log_path)
+    accs.Reload()
+
+    scalars = []
+    name = []
+    order = []
+    for a in accs._accumulators:
+        acc = accs._accumulators[a]
+        s = acc.Scalars('val_acc')
+        scalars.append(s)
+        clu = a.split('_')[3]
+        wind = a.split('_')[1]
+        order.append([clu, wind])
+        n = '_'.join(a.split('_')[:-1])
+        name.append(n)
+
+    scalars = [x for _, x in sorted(sorted(zip(order, scalars), key=lambda x: x[0][0]), key=lambda x:x[0][1])]
+    name = [x for _, x in sorted(sorted(zip(order, name), key=lambda x: x[0][0]), key=lambda x:x[0][1])]
+
+    x_list = []
+    y_list = []
+    x_list_raw = []
+    y_list_raw = []
+    for scalar in scalars:
+        x = [int(s.step) for s in scalar]
+        y = [s.value for s in scalar]
+
+        # smooth curve
+        x_sm = np.array(x)
+        y_sm = np.array(y)
+        x_ = np.linspace(x_sm.min(), x_sm.max(), 200)
+        y_ = spline(x, y, x_)
+        x_list.append(x_)
+        y_list.append(y_)
+
+    figure = plt.figure(figsize=(16,8))
+    ax = plt.subplot(111)
+
+    for i in range(len(x_list)):
+        plt.title(title)
+        plt.plot(x_list[i], y_list[i])
+    ax.legend(labels=name, bbox_to_anchor=(1.12, 1), frameon=True, edgecolor='black', title = 'Legend')
+    plt.savefig(fname=fname+"plot.png")
+    plt.close(figure)
+
+
+if __name__ == '__main__':
[…]

### 2018-07-06 dlp/keras_network.py
changes keras_network

@@ -7,7 +7,7 @@ Created on Sun Jun 10 15:31:34 2018
 
 import time
 from keras.models import Model
-from keras.layers import Input,Embedding, Conv1D, Conv2D, Activation, Dot, Lambda, Permute, Concatenate
+from keras.layers import Input,Embedding, Conv1D, Conv2D, Activation, Dot, Lambda, Permute, Concatenate, Add, Masking
 import keras.backend as K
 import tensorflow as tf
 from keras.callbacks import TensorBoard, EarlyStopping
@@ -53,48 +53,65 @@ class ModelBuilder(object):
         return Concatenate()(out_b)
 
     def buildModel(self, clu, window_size):
-        q_1= Input(shape=(self.q_length,), dtype='int32')
-        q_2= Input(shape=(self.q_length,), dtype='int32')    
-        
+        q_1= Input(shape=(None,), dtype='int32')
+        q_2= Input(shape=(None,), dtype='int32')
+
         lookup=Embedding(self.vocabulary_size, self.embedding_size, input_length=self.q_length, embeddings_initializer=self.embeddings_initialize, trainable=False)
         lookup_layer_1= lookup(q_1)
         lookup_layer_2= lookup(q_2)
-
-        # q1_emb and q2_emb (?, q_length * embedding)
-        #expand = Lambda(lambda x: K.expand_dims(x, axis=-1))
-        #expand = Reshape(target_shape=(self.q_length * self.embedding_size, 1))
-        #expanded_layer_1 = Reshape(target_shape=(self.q_length * self.embedding_size, 1))(lookup_layer_1)
-        #expanded_layer_2 = Reshape(target_shape=(self.q_length * self.embedding_size, 1))(lookup_layer_2)
-        #print("Expand shape: ", expanded_layer_1.shape)
 
         conv1d = Conv1D(filters=clu, kernel_size=window_size, activation='tanh', padding='valid')
         conv_layer_1 = conv1d(lookup_layer_1)
         conv_layer_2 = conv1d(lookup_layer_2)
 
-
-        # conv2d=Conv2D(filters=self.clu, kernel_size=(self.window_size, self.embedding_size), activation='tanh', padding='valid')
-        # conv_layer_1=conv2d(expanded_layer_1)
-        # conv_layer_2=conv2d(expanded_layer_2)
-        # print("Conv shape: ", conv_layer_1.shape)
-
         sum_layer = Lambda(lambda x: K.sum(x,axis=1))
[…]

### 2018-07-06 dlp/BatchGenerator.py
batch generator

@@ -1,0 +1,24 @@
+import numpy as np
+from keras.preprocessing.sequence import pad_sequences
+import time
+
+class KerasBatchGenerator(object):
+
+    def __init__(self, x1, x2, y,  batch_size):
+        self.x1 = x1
+        self.x2 = x2
+        self.y=y
+        self.batch_size = batch_size
+        self.current_idx = 0
+
+    def generate(self):
+        while True:
+            if self.current_idx + self.batch_size >= len(self.x1):
+                # reset the index back to the start of the data set
+                self.current_idx = 0
+
+            x_1 = pad_sequences(self.x1[self.current_idx:self.current_idx+self.batch_size], padding='post')
+            x_2 = pad_sequences(self.x2[self.current_idx:self.current_idx + self.batch_size], padding='post')
+
+            y = self.y[self.current_idx:self.current_idx+self.batch_size]
+            yield ([x_1, x_2], y)

### 2018-07-11 dlp/tokenizer.py
tokenizer

@@ -1,48 +1,63 @@
-# -*- coding: utf-8 -*-
-"""
-Created on Wed Jun  6 15:25:52 2018
-
-@author: lucas
-"""
-#%%
 from bs4 import BeautifulSoup
 from nltk import word_tokenize
 import re
 import spacy
+from spacy.tokenizer import Tokenizer 
+from spacy.pipeline import Pipe
+from selectolax.parser import HTMLParser
+from lxml import etree
 
 import dlp.util as util
 
-class Tokenizer(object):
+class TokenizerPosts(object):
     
     def __init__(self, df):
         #super(Tokenizer, self).__init__()
-        self.soups=[BeautifulSoup(q, 'html5lib') for q in list(df["Text"])]
-
+        self.soups=list(df["Text"])
+        #self.soups = df
     
-    def __replace_links(self, soup):
-        """
-        Replace the links of a single soup with a unique string
-        """
-        for link in soup.find_all('a'):
-            link.string='thistokenisalink'
-        #return soup
+#    def __replace_links(self, soup):
+#        """
+#        Replace the links of a single soup with a unique string
+#        """
+#        for link in soup.find_all('a'):
+#            link.string='thistokenisalink'
+#        #return soup
     
     
     def __replace_code(self, soup):
         """
         Replace the code of a single soup with a unique string
         """
-        for code in soup.find_all('code'):
-            code.string='thistokeniscode'
-        #return soup
+        code=re.compile(util.CODE)
+        return re.sub(code, 'thistokeniscode', soup)
     
+    def __deletetabulation(self, soup):
+        """
+        Delete any tabulation as \n, \t, .. 
+        """
+        tab = re.compile(util.TAB)
+        return re.sub(tab, '', soup)
     
+    def __deletenochar(self, soup):
+        """
+        Delete any no char as £,$,%,..
+        """
+        nochar= re.compile(util.NOCHAR)
+        if nochar.fullmatch(soup)==None:
+            #soup=re.sub(nochar, '', soup)        
+            return soup
+    
+
+
     def __replace_time(self, soup_text):
         """
         Replace the time format in the text of a single soup with a unique string
         """
         time=re.compile(util.TIME)
-        return re.sub(time, 'thistokenistime', soup_text)
+        if time.fullmatch(soup_text)!=None:
+            soup_text=re.sub(time, 'thistokenistime', soup_text)        
+        return soup_text
     
     
[…]

### 2018-07-11 dlp/util.py

@@ -35,3 +35,6 @@ VERSION= r'(\d+\.\d+(.\d+)*)|(\S*\d+\S*)+'
 PATH= r'(~|\w*|.)?(/\S*)+'
 HEXADECIMAL= r'0x[0-9a-fA-F]+'
 VARIABLE= r'([a-zA-Z0-9]*_+[a-zA-Z0-9]*)+'
+CODE= r'<code>.*</code>'
+TAB = r'(\n)+'
+NOCHAR = r'(£|\$|%|&|\^|#|§|@|\<|\>|\\)+'

### 2018-07-11 main_dataset_generation.py

@@ -15,7 +15,7 @@ from dlp.data_filter import XMLDataFilter
 from dlp.data_parser import XMLtoPandasParser
 from dlp.non_dup_generator import NonDupGenerator
 from dlp.train_test_val_generation import TrainTestValGenerator
-from dlp.tokenizer import Tokenizer
+from dlp.tokenizer import TokenizerPosts
 
 def drop_inconsistent_links(posts_df, links_df):
     cond1 = pd.isnull(posts_df.loc[links_df['Post1Id'].values]['Tokens'].values)
@@ -24,15 +24,14 @@ def drop_inconsistent_links(posts_df, links_df):
     return links_df[cond]
 
 def main():
-    
-    global posts_df
-    global dup_df
-    dup_df.columns=['isDuplicate', 'Post1Id', 'Post2Id']
-    if type(posts_df.index) == pd.RangeIndex: 
-        posts_df.set_index('Id', inplace=True)
+#    global posts_df
+#    global dup_df
+#    dup_df.columns=['isDuplicate', 'Post1Id', 'Post2Id']
+#    if type(posts_df.index) == pd.RangeIndex: 
+#        posts_df.set_index('Id', inplace=True)
     print("Loading data...")
     start = time.clock()
-    """
+    
     #laod the data as xml objects
     xml_loader = XMLDataLoader()
     posts_root = xml_loader.load_posts()
@@ -47,7 +46,7 @@ def main():
     xml_to_pandas_parser = XMLtoPandasParser()
     posts_df = xml_to_pandas_parser.to_dataframe_posts(posts_root)
     dup_df = xml_to_pandas_parser.to_dataframe_links(links_root)
-    """
+    
     load_time = time.clock() - start
     print("TIME TO LOAD AND PREPROCESS THE DATA: ", load_time)
     
@@ -56,8 +55,9 @@ def main():
     start=time.clock()
     print("Tokenizing text..")
     
-    tokenizer = Tokenizer(posts_df)
+    tokenizer = TokenizerPosts(posts_df)
     posts_df["Tokens"] = tokenizer.tokenize()
+    #result = tokenizer.tokenize()
     
     tokenization_time= time.clock() - start
     print("TIME TO TOKENIZE THE TEXT: ", tokenization_time)

### 2018-07-11 paper/paper_final.tex
Experiments setup paper [da finire]

@@
 
-Then we noticed that some patterns are very frequent but not so relevant in their different form. Therefore we had some other precautions:
+Then we noticed that some patterns are very frequent but not so relevant in their different forms. Therefore we had some other precautions:
 \begin{itemize}
@@
 \paragraph{Experiments setup.}
+First of all we have trained the model with pretrained English Wikipedia's embeddings \footnote{\url{http://nlp.stanford.edu/data/glove.6B.zip}}.
+In our model we have identified the following hyperparameters:
+\begin{itemize}
+	\item $cl_{u}$, that is the number of units of the one-dimensional convolutional layer
+	\item $k$, that is the number of successive words within a window
+\end{itemize}
+Since the hyperparameters are continuous and the hyperparameter space can be very huge, we decide to use a Gaussian Process to approximate the validation accuracy function.
+At each iteration of this process we sample the hyperparameters from Gaussian prior, we train the model with this configuration and we update the Gaussian prior with the validation accuracy of the trained model.
+Moreover we use Early Stopping technique in order to avoid overfitting.
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=1\linewidth]{img/wiki.png}
+\end{center}
+\caption{Validation accuracy depending on the hyperparameters.}
+\label{fig:wiki}
+\end{figure}
+In Figure \ref{fig:wiki} is represented the validation accuracy resulted from different combinations during the hyperparameters tuning.
+For the sake of clarity we show in the figure only the best combination for each window size, but we observe that increasing too much the number of units of the convolutional layer, $cl_{u}$, provides worst performance.
+As the figure indicates, decreasing the window size, $k$, provides improvements.
+\\~\\
+After that we train the model with AskUbuntu embeddings, in order to evaluate the impact of in-domain word embeddings on the network's performance. 
+\begin{table}
+\begin{center}
+\begin{tabular}{|l|c|}
+\hline\hline
+Word embedding & Validation accuracy \\
+\hline\hline
+Wikipedia & Frumpy \\
+AskUbuntu & Frobbly \\
+\hline
+\end{tabular}
+\end{center}
+\caption{Validation Accuracy with word embedding pretrained on different corpora.}
+\label{table:accuracy}
+\end{table}
+As the Table \ref{table:accuracy} shows, using in-domain embeddings is more beneficial for the network. \\
+In both experiments we use Adam optimizer with learning rate $ lr=0.002 $. \\~\\
+Lastly, we experiment to add another embedding layer, initialized with AskUbuntu's embeddings and trainable. In this case we observe approximately one percent improvement.
 

### 2018-07-11 paper/paper_final.tex
Experiments setup paper

@@
 Moreover we use Early Stopping technique in order to avoid overfitting.
-\begin{figure}[t]
-\begin{center}
-\includegraphics[width=1\linewidth]{img/wiki.png}
-\end{center}
-\caption{Validation accuracy depending on the hyperparameters.}
-\label{fig:wiki}
-\end{figure}
+
 In Figure \ref{fig:wiki} is represented the validation accuracy resulted from different combinations during the hyperparameters tuning.
@@
 \\~\\
-After that we train the model with AskUbuntu embeddings, in order to evaluate the impact of in-domain word embeddings on the network's performance. 
+After that we train the model with AskUbuntu embeddings, in order to evaluate the impact of in-domain word embeddings on the network's performance. \\
+As the Table \ref{table:accuracy} shows, using in-domain embeddings is more beneficial for the network. \\
+In both experiments we use Adam optimizer with learning rate $ lr=0.002 $. \\~\\
+Lastly, we experiment to add another embedding layer, initialized with AskUbuntu's embeddings and trainable.
+In this case we observe approximately one percent improvement.
+In the Figure \ref{fig:embeddings} it is indicated as Ubuntu multichannel.
 \begin{table}
@@
 \begin{tabular}{|l|c|}
-\hline\hline
+\hline
 Word embedding & Validation accuracy \\
-\hline\hline
-Wikipedia & Frumpy \\
-AskUbuntu & Frobbly \\
+\hline
+Wikipedia & 86\% \\
+AskUbuntu & 90\% \\
 \hline
@@
 \end{table}
-As the Table \ref{table:accuracy} shows, using in-domain embeddings is more beneficial for the network. \\
-In both experiments we use Adam optimizer with learning rate $ lr=0.002 $. \\~\\
-Lastly, we experiment to add another embedding layer, initialized with AskUbuntu's embeddings and trainable. In this case we observe approximately one percent improvement.
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=90mm, height= 55mm, scale=1]{img/wiki.png}
+\end{center}
+\caption{Validation accuracy depending on the hyperparameters.}
+\label{fig:wiki}
+\end{figure}
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=90mm, height= 55mm, scale=1]{img/embeddings_accuracy.png}
+\end{center}
+\caption{Validation Accuracy depending on the domain of the word embeddings and ????}
+\label{fig:embeddings}
+\end{figure}
 

### 2018-07-12 paper/paper_final.tex
modified paper

@@
 Ask Ubuntu is a community for Ubuntu users and developers, and it is part of the Stack Exchange Q\&A communities.
-The users of these communities can ask and answer ques- tions, and vote up and down both questions and answers.
+The users of these communities can ask and answer que tions, and vote up and down both questions and answers.
 Users with high reputation become moderators and can label a new question as a duplicate to an existing question.
@@
 Moreover we use Early Stopping technique in order to avoid overfitting.
+\\
+After that, in order to evaluate the impact of in-domain word embeddings on the network's performances, we train the model with AskUbuntu embeddings. \\
+In both experiments we use Adam optimizer initialized with learning rate $ lr=0.002 $.
 
-In Figure \ref{fig:wiki} is represented the validation accuracy resulted from different combinations during the hyperparameters tuning.
-For the sake of clarity we show in the figure only the best combination for each window size, but we observe that increasing too much the number of units of the convolutional layer, $cl_{u}$, provides worst performance.
-As the figure indicates, decreasing the window size, $k$, provides improvements.
+\paragraph{Results and discussion.}
+As the Table \ref{table:accuracy} shows, the model trained using in-domain embeddings outperform that trained using Wikipedia's embeddings. \\
+In Figure \ref{fig:wiki} is represented the validation accuracy resulted from different combinations of hyperparameters values.
+For the sake of clarity we show in the figure only the best $cl_{u}$ value for each window size, but we observe that increasing too much the number of units of the convolutional layer, $cl_{u}$, provides worst performances.
+As the figure indicates, smaller window sizes, provides the best performances.
 \\~\\
-After that we train the model with AskUbuntu embeddings, in order to evaluate the impact of in-domain word embeddings on the network's performance. \\
-As the Table \ref{table:accuracy} shows, using in-domain embeddings is more beneficial for the network. \\
-In both experiments we use Adam optimizer with learning rate $ lr=0.002 $. \\~\\
 Lastly, we experiment to add another embedding layer, initialized with AskUbuntu's embeddings and trainable.
@@
 \end{figure}
-
-\paragraph{Results and discussion.}
 

### 2018-07-12 paper/paper_final.tex
paper updates

@@
 
-\cvprfinalcopy % *** Uncomment this line for the final submission
+%\cvprfinalcopy % *** Uncomment this line for the final submission
 
@@
 This work is the replication of \cite{bogdanova2015detecting}: we basically try to perform the same experiments and compare our results with theirs.
-The replication turned to be not straightforward since some crucial implementation details are missing in the Bogdanova et al.'s description.
+The replication turned not to be straightforward since some crucial implementation details are missing in the Bogdanova et al.'s description.
 Hence, we have found quite stimulating to replicate this paper filling the holes with our own ideas.
 In particular, our efforts focused mainly on the following three aspects that were not explicitly treated in the paper: unequal text length, the type of convolution and the training of in-domain word embeddings.
-The final results we obtained are quite close to the our target; whereas the optimal parameters values of the network are quite different from \cite{bogdanova2015detecting}.
+The final results we obtained are quite close to our target; even the optimal hyperparameters values of the network are very similar to the ones in \cite{bogdanova2015detecting}.
 It is worth clarifying that, since we used domain-specific data for both training and testing the model, the obtained performances are guaranteed to hold only for pairs of questions coming from that specific domain.
@@
 \\
-
-In general, the results obtained by our implementation are very close to the ones of the replicated paper.
-Surprisingly, as we will discuss in Section 4, the main differences in the results are about the optimal hyper-parameter values of the network.\\
+In general, both results and optimal hyperparameter values obtained by our implementation are very close to the ones of the replicated paper.\\
 The authors of the paper accurately described the architecture of the network, but many crucial details of the model are missing in their description.
 Hence, we have found quite stimulating to replicate this paper filling the holes with our own ideas.
-In particular, our efforts focused mainly on the following three aspects that were not explicitly treated in the paper:
+In particular, our efforts focused mainly on the following four aspects that were not explicitly treated in the paper:
     \paragraph{Handling questions of different sizes.}
@@
     The paper does not provide any information about the model used to train in-domain word embeddings.
-Initially, we tried to build our own \emph{word2vec} model \cite{mikolov2013distributed} to generate word-embeddings using as training data the same dataset used to train the main network \footnote{To do so we followed this good tutorial: \url{http://adventuresinmachinelearning.com/word2vec-keras-tutorial/}}.
+Initially, we tried to build our own \emph{word2vec} model \cite{mikolov2013distributed} to generate word-embeddings using the same dataset employed to train the main network \footnote{To do so we followed this good tutorial: \url{http://adventuresinmachinelearning.com/word2vec-keras-tutorial/}}.
 However, the training of this network turned out to be very slow and resulting embeddings performed poorly.
 \\
-    We, then, decided to use Gensim, a very simple library which generates word-embeddings given the training data.
+    We, then, decided to use Gensim \footnote{\url{https://radimrehurek.com/gensim/index.html}}, a very simple library which generates word-embeddings given the training data.
 The resulting embeddings performed very well, allowing the main network to achieve up to 90\% of accuracy on the validation set.
+    	\paragraph{CNN Multi-channel}
+    	As suggested by Kim in \cite{kim2014convolutional}, we also tried a simple variant of the CNN proposed in \cite{bogdanova2015detecting}.
+The first hidden layer of this network has two ``channels'' of word-embeddings: one that is kept static during training and one that is fine-tuned via backpropagation.
+This modification brings an improvement of around 1\% to the performances of the network.
 
@@
 In this section we present our strategy for detecting semantically equivalent questions.
-In subsection 3.1, we describe in detail the architecture of the Neural Network.
+In Subsection 3.1, we describe in detail the architecture of the Neural Network.
 Then, in subsequent subsections, we focus on the decisions we have made about the things left unspecified by Bogdanova et al.
@@
 \subsection{Neural Network Architecture}
-As detailed in Figure \ref{fig:network}, the input for the network is tokenized text strings of the two questions.
+As detailed in Figure \ref{fig:network}, the inputs for the network are tokenized text strings of the two questions.
 In the first step, the CNN transforms words into real valued feature vectors, also known as \emph{word embeddings}.
@@
 \begin{center}
-%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
 \includegraphics[width=0.8\linewidth]{img/network.png}
@@
 \label{fig:network}
-%\label{fig:onecol}
 \end{figure}
@@
 \item \textbf{The vocabulary}: a dictionary $V$ associating each word of the corpora used to train the embeddings to an integer index.
-In this vocabulary, we must also reserve an index for all the words which are not present in the vocabulary.
+In this vocabulary, we must also reserve an index for all the words which are not present in the vocabulary itself.
 Best practices suggest to have the index $0$ for the \emph{unknown} words and then having the other indexes ordered by most common words.
@@
 Hence, the output is a matrix $X_0 \in \mathbb{R}^{N \times d}$.\\
+In the simplest implementation of the network, the matrix $W_0$ is kept static during the training.
+In Section \ref{multichannel} we describe a simple modification in which this matrix becomes trainable.\\
 Notice that using pre-trained word embeddings, implies that the values of both the $d$ and $|V|$ have been already decided by those who trained the matrix $W_0$.
@@
 All the techniques that can be used to tackle this issue force us to introduce new hyper-parameters or work-around in our model which are not fundamental for  the NLP task but are present to only handle unequal text lengths.\\
-We decided to try two of these techniques, which we found out to be the best practices:
+We decided to try two of these techniques, which are considered best practices:
 \begin{itemize}
@@
 Therefore, our network accepts as input only questions of the same length.\\
-The experimental results show that the \emph{max} approach provides the best performances.
-This is probably due to the fact that the \emph{mean} approach is very likely to drop important semantic information from the sentence.
-It is worth mentioning that, in order for the \emph{max} approach to perform at its best, it can be a good choice dropping the outliers, i.e.
-the questions that are too long with respect to the other observations.
+
 %-------------------------------------------------------------------------
@@
 To implement the convolution described in Section 3.1.2., we decided to use a 1-dimensional convolutional layer.
-The reason behind this choice is that, as images are seen as three input maps (R,G,B) where each map is a 2-dimensional array (matrix) with height and width, similarly text can be seen as $d$ input maps where each map has only one dimension which is the length of the question.
+The reason behind this choice is that, as images are seen as three input maps (R,G,B) where each map is a 2-dimensional array (height and width), similarly, text can be seen as $d$ input maps where each map has only one dimension which is the length of the question.
 This interpretation of the 1-dimensional convolution is exemplified in Figure \ref{fig:conv}.\\
@@
 %-------------------------------------------------------------------------
-\subsection{In-domain Word Embeddings}    
-The training of in-domain word embeddings was one of the hardest task of our work. 
+\subsection{CNN Multichannel}    \label{multichannel}
+Taking inspiration from \cite{kim2014convolutional}, we tried a simple modification of the network proposed by \cite{bogdanova2015detecting}.
+The modified model has two matrices of word embeddings.
+Each matrix of embeddings is treated as a ‘channel’ and each filter is applied to both channels, but gradients are backpropagated only through one of the channels.
+Hence the model is able to fine-tune one matrix of embeddings while keeping the other static.
+Both channels are initialized with pre-trained word embeddings.
+\\
+The outputs of the first hidden layer, in this case, are two matrices $X_0', X_0'' \in \mathbb{R}^{N \times d}$.
+The matrix $X_0 \in \mathbb{R}^{N \times 2d}$ will be the horizontal concatenation of $X_0'$ and $X_0''$.
+
 %------------------------------------------------------------------------
@@
 Tokenization is the process of breaking up a given text, in this case every question, into units called tokens.
-The tokens may be words or number or punctuation mark: we decide to consider only words and to disregard those tokens that are punctuation, symbols, tabulation, white spaces, articles and prepositions.
+The tokens may be words or number or punctuation mark: we decide to consider only words and to disregard those tokens that are punctuation, articles and prepositions.
 For each word we took only its lemma.
@@
 \paragraph{Results and discussion.}
-As the Table \ref{table:accuracy} shows, the model trained using in-domain embeddings outperform that trained using Wikipedia's embeddings. \\
+The experimental results show that the \emph{max} approach provides the best performances.
+This is probably due to the fact that the \emph{mean} approach is very likely to drop important semantic information from the sentence.
+However, it is worth mentioning that, in order for the \emph{max} approach to perform at its best, it is  definitely a good choice dropping the outliers, i.e.
+the questions that are too long with respect to the other observations.
+Figure \ref{fig:lens} shows the distribution of the question lengths of our dataset: it is evident that more than 95\% of the questions contains less than 400 words.
+Hence, we decide to drop the remaining 5\% of the questions.\\
 In Figure \ref{fig:wiki} is represented the validation accuracy resulted from different combinations of hyperparameters values.
 For the sake of clarity we show in the figure only the best $cl_{u}$ value for each window size, but we observe that increasing too much the number of units of the convolutional layer, $cl_{u}$, provides worst performances.
-As the figure indicates, smaller window sizes, provides the best performances.
-\\~\\
-Lastly, we experiment to add another embedding layer, initialized with AskUbuntu's embeddings and trainable.
-In this case we observe approximately one percent improvement.
-In the Figure \ref{fig:embeddings} it is indicated as Ubuntu multichannel.
+As the figure indicates, smaller window sizes, provides the best performances.\\
+Figure \ref{fig:embeddings} shows that, the addition of a trainable embedding layer, provides a performance improvement of around 1\%.
+The figure also highlights that (as stated in Table \ref{table:accuracy}) the model trained with in-domain embeddings outperform that trained using Wikipedia's embeddings.\\
+The best model possible is, therefore, the CNN Multi-Channel initialized using in-domain word embeddings with $cl_u=300$ and $k=2$. It achieves 89\% accuracy on the test set.
 \begin{table}
@@
 AskUbuntu & 90\% \\
+AskUbuntu multichannel & ??\% \\
 \hline
@@
 \end{table}
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=90mm, height= 55mm, scale=1]{img/Histogram.png}
+\end{center}
+\caption{Distribution of question lengths.}
+\label{fig:lens}
+\end{figure}
 \begin{figure}[t]
@@
 \end{center}
-\caption{Validation Accuracy depending on the domain of the word embeddings and ????}
+\caption{Validation Accuracy using Wikipedia's embeddings, AskUbuntu embeddings and CNN Multi-channel}
 \label{fig:embeddings}
@@
 \section{Conclusion} 
-
-%\begin{figure*}[t]
-%\begin{center}
-%\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-%\end{center}
-%   \caption{Example of a short caption, which should be centered.}
-%\label{fig:short}
-%\end{figure*}
-
-%-------------------------------------------------------------------------
-\section*{Acknowledgements}
-
-%-------------------------------------------------------------------------
-\appendix
-\section{Supplementary Material}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{|l|c|}
-%\hline
-%Method & Frobnability \\
-%\hline\hline
-%Theirs & Frumpy \\
-%Yours & Frobbly \\
-%Ours & Makes one's heart Frob\\
-%\hline
-%\end{tabular}
-%\end{center}
-%\caption{Results.   Ours is better.}
-%\end{table}
+This work attempts to replicate the Bogdanova et al.' paper \cite{bogdanova2015detecting}.
+The obtained results are very close to our target.
+The in-domain word embeddings perform better than general-ones.
+The \emph{max} approach results to be the best solution for the problem of unequal text lengths.
+The CNN Multi-channel model brings a performance improvement of 1\%.
+The final model achieves 89\% accuracy on the test set.\\
+A possible extension of this work could be to use an LSTM approach to solve the problem of unequal text lengths. Moreover, other deeper architectures could be explored.
 

### 2018-07-13 paper/paper_final.tex
modified conclusion paper

@@
 AskUbuntu & 90\% \\
-AskUbuntu multichannel & ??\% \\
+AskUbuntu multichannel & 91\% \\
 \hline
@@
 \section{Conclusion}
-This work attempts to replicate the Bogdanova et al.' paper \cite{bogdanova2015detecting}.
-The obtained results are very close to our target.
-The in-domain word embeddings perform better than general-ones.
-The \emph{max} approach results to be the best solution for the problem of unequal text lengths.
-The CNN Multi-channel model brings a performance improvement of 1\%.
-The final model achieves 89\% accuracy on the test set.\\
+
+In this paper, we attempts to replicate the Bogdonova et al.
+paper \cite{bogdanova2015detecting} that propose a method for identifying semantically equivalent questions based on a convolutional neural network.
+We solve the problem of unequal text legths by considering the \emph{max} length, which reaches better performance with respect to the mean approach.
+We experimentally show that the proposed CNN achieves high accuracy especially when the word embeddings are pre-trained on in-domain data.
+In particular we found out that the CNN Multi-channel model brings a performance improvement of one-percent with respect to the model with only one matrix of word embeddings .
+This model achieves 89\% accuracy on the test set, that is a result very close to the one of our target.\\
 A possible extension of this work could be to use an LSTM approach to solve the problem of unequal text lengths. Moreover, other deeper architectures could be explored.

### 2018-07-13 paper/paper_final.tex
paper coherently in present tense

@@
 This work is the replication of \cite{bogdanova2015detecting}: we basically try to perform the same experiments and compare our results with theirs.
-The replication turned not to be straightforward since some crucial implementation details are missing in the Bogdanova et al.'s description.
-Hence, we have found quite stimulating to replicate this paper filling the holes with our own ideas.
-In particular, our efforts focused mainly on the following three aspects that were not explicitly treated in the paper: unequal text length, the type of convolution and the training of in-domain word embeddings.
-The final results we obtained are quite close to our target; even the optimal hyperparameters values of the network are very similar to the ones in \cite{bogdanova2015detecting}.
-It is worth clarifying that, since we used domain-specific data for both training and testing the model, the obtained performances are guaranteed to hold only for pairs of questions coming from that specific domain.
+The replication is made harder by the fact that some crucial implementation details are missing in the Bogdanova et al.'s description.
+Hence, we find quite stimulating to replicate this paper filling the holes with our own ideas.
+In particular, our efforts focus mainly on the following three aspects that were not explicitly treated in the paper: unequal text length, the type of convolution and the training of in-domain word embeddings.
+\\
+Moreover, we attempt to make the simple modification to the network, suggested by Kim \cite{kim2014convolutional}. This simple change increases the validation accuracy by about 1\%. \\
+The final results are quite close to our target; even the optimal hyper-parameters values of the network are very similar to the ones in \cite{bogdanova2015detecting}.
+It is worth clarifying that, since we use domain-specific data for both training and testing the model, the obtained performances are guaranteed to hold only for pairs of questions coming from that specific domain.
 \end{abstract}
@@
 Finally, pairs of questions are scored using a similarity function.
-The most interesting experimental result is the evaluation of in-domain word embeddings versus the word embeddings generated using all of the English Wikipedia.
-In particular, they shown that domain-specific word embeddings achieve higher performances.
+The most interesting experimental result is the evaluation of in-domain word embeddings against the word embeddings generated using all of the English Wikipedia.
+In particular, they show that domain-specific word embeddings achieve higher performances.
 \\
-In general, both results and optimal hyperparameter values obtained by our implementation are very close to the ones of the replicated paper.\\
-The authors of the paper accurately described the architecture of the network, but many crucial details of the model are missing in their description.
-Hence, we have found quite stimulating to replicate this paper filling the holes with our own ideas.
-In particular, our efforts focused mainly on the following four aspects that were not explicitly treated in the paper:
+In general, both validations accuracy and optimal hyper-parameter values obtained by our implementation are very close to the ones of the replicated paper.\\
+The authors of \cite{bogdanova2015detecting} accurately describe the architecture of the network, but many crucial details of the model are missing in their description.
+Hence, we find quite stimulating to replicate this paper filling the holes with our own ideas.
+In particular, our efforts focus mainly on four aspects that are not explicitly treated in \cite{bogdanova2015detecting}.
+In the following we just introduce them; they are further analyzed in Section 3.
     \paragraph{Handling questions of different sizes.}
@@
 Nevertheless, they do not specify the way they solved this issue.
-We, therefore, tried to fix the length of each question to the \textbf{maximum} and to the \textbf{mean} length of all the questions.
-The first approach resulted to yield the greater accuracy.
+We, therefore, try to fix the length of each question to the \textbf{maximum} and to the \textbf{mean} length of all the questions.
+The first approach does yield the greatest accuracy.
     \paragraph{The type of convolution.}
-    For the implementation of our network we used a 1-dimensional convolution.
+    For the implementation of our network we use a 1-dimensional convolution.
 Indeed, text can be seen as images with the input maps having only one dimension (height, without width) corresponding to the question length and where the number of input maps is nothing but the size of the word embeddings.
@@
     \paragraph{The training of in-domain word embeddings.}
-    The paper does not provide any information about the model used to train in-domain word embeddings.
-Initially, we tried to build our own \emph{word2vec} model \cite{mikolov2013distributed} to generate word-embeddings using the same dataset employed to train the main network \footnote{To do so we followed this good tutorial: \url{http://adventuresinmachinelearning.com/word2vec-keras-tutorial/}}.
-However, the training of this network turned out to be very slow and resulting embeddings performed poorly.
+    The paper does not provide any information about the model adopted to train in-domain word embeddings.
+Initially, we tried to build our own \emph{word2vec} model \cite{mikolov2013distributed} trained with the same dataset employed to train the main network \footnote{To do so we followed this good tutorial: \url{http://adventuresinmachinelearning.com/word2vec-keras-tutorial/}}.
+However, the training of this network turned out to be very slow and the resulting embeddings performed poorly.
 \\
     We, then, decided to use Gensim \footnote{\url{https://radimrehurek.com/gensim/index.html}}, a very simple library which generates word-embeddings given the training data.
-The resulting embeddings performed very well, allowing the main network to achieve up to 90\% of accuracy on the validation set.
+The resulting embeddings perform very well, allowing the main network to achieve up to 90\% of accuracy on the validation set.
     	\paragraph{CNN Multi-channel}
-    	As suggested by Kim in \cite{kim2014convolutional}, we also tried a simple variant of the CNN proposed in \cite{bogdanova2015detecting}.
+    	As suggested by Kim in \cite{kim2014convolutional}, we also investigate a simple variant of the CNN proposed in \cite{bogdanova2015detecting}.
 The first hidden layer of this network has two ``channels'' of word-embeddings: one that is kept static during training and one that is fine-tuned via backpropagation.
@@
 In \cite{kim2014convolutional}, Kim proposes a very simple CNN architecture trained on top of pre-trained word vectors.
-He experimented the same network on 7 different sentence-level classification tasks and, for each task, he compared the obtained results with the state-of-the-art: the CNN approach improved upon the state-of-the-art on 4 out of 7 tasks.
+He experiments the same network on 7 different sentence-level classification tasks and, for each task, he compares the obtained results with the state-of-the-art: the CNN approach improves upon the state-of-the-art on 4 out of 7 tasks.
 Moreover, he proposes a slight modification of the network with 2 channels of word vectors: one that is kept static during the training and one that is fine-tuned via backpropagation.
-Although not explicitly stated, we think this has been the main contribution of \cite{bogdanova2015detecting} as the network architecture is pretty much the same.
+Although not explicitly stated, we think this is the main contribution of \cite{bogdanova2015detecting} as the network architecture is pretty much the same.
 The Kim's architecture represents the state-of-the-art on many NLP sentence classification tasks and it is often used as a layer of more complex networks which need to compute sentence-level distributed vectors representation.
@@
 A different but still interesting approach to the problem of text classification, is described in \cite{zhang2015character}.
-In this article, the authors explore treating text as a kind of raw signal at character level, and applying temporal (one-dimensional) Convolutional Network to it.\\
+In this article, the authors explore treating text as a kind of raw signal at character level, and applying temporal (1-dimensional) Convolutional Network to it.\\
 Different CNN architectures are used for solving a wide range of NLP tasks and many encouraging results have been already achieved.
 Yih et al.
-\cite{yih2014semantic} introduced a novel semantic similarity model based on a CNN architecture for the task of answering single-relation factual questions.
+\cite{yih2014semantic} introduce a novel semantic similarity model based on a CNN architecture for the task of answering single-relation factual questions.
 Hu et al.
-\cite{hu2014convolutional} proposed a CNN architecture for hierarchical sentence modeling and sentence matching.
-Convolution has been also used by Dos Santos et al.
+\cite{hu2014convolutional} propose a CNN architecture for hierarchical sentence modeling and sentence matching.
+Convolution is also used by Dos Santos et al.
 \cite{dos2014deep} for sentiment analysis of short texts that jointly uses character-level, word-level and sentence-level information.\\
@@
 All the techniques that can be used to tackle this issue force us to introduce new hyper-parameters or work-around in our model which are not fundamental for  the NLP task but are present to only handle unequal text lengths.\\
-We decided to try two of these techniques, which are considered best practices:
+Here we explore two of these techniques, which are considered best practices:
 \begin{itemize}
@@
 \end{itemize}
-To keep the architecture of our network as simpler as possible we decided to apply this techniques as a preprocessing phase, without adding any further layer to the network architecture.
+To keep the architecture of our network as simpler as possible we apply this techniques as a preprocessing phase, without adding any further layer to the network architecture.
 Therefore, our network accepts as input only questions of the same length.\\
@@
 
-To implement the convolution described in Section 3.1.2., we decided to use a 1-dimensional convolutional layer.
+To implement the convolution described in Section 3.1.2., we use a 1-dimensional convolutional layer.
 The reason behind this choice is that, as images are seen as three input maps (R,G,B) where each map is a 2-dimensional array (height and width), similarly, text can be seen as $d$ input maps where each map has only one dimension which is the length of the question.
-This interpretation of the 1-dimensional convolution is exemplified in Figure \ref{fig:conv}.\\
+This interpretation of the 1-dimensional convolution for text data is exemplified in Figure \ref{fig:conv}.\\
 After applying vertically the sum operation to the output of this layer, the resulting vector is exactly the one described by Equation \ref{eq:conv}
@@
 \subsection{CNN Multichannel}    \label{multichannel}
-Taking inspiration from \cite{kim2014convolutional}, we tried a simple modification of the network proposed by \cite{bogdanova2015detecting}.
+Taking inspiration from \cite{kim2014convolutional}, we investigate a simple modification of the network proposed by \cite{bogdanova2015detecting}.
 The modified model has two matrices of word embeddings.
@@
 Ask Ubuntu is a community for Ubuntu users and developers, and it is part of the Stack Exchange Q\&A communities.
-The users of these communities can ask and answer que tions, and vote up and down both questions and answers.
+The users of these communities can ask and answer questions, and vote up and down both questions and answers.
 Users with high reputation become moderators and can label a new question as a duplicate to an existing question.
@@
 We use Ask Ubuntu data dump \footnote{ \url{https://archive.org/download/stackexchange}} provided in April 2018, that contains posts from 2010 to March 2018.
-From the data dump we have selected only the posts that are questions, the amount of questions is 285651.
-We extract all question pairs linked as duplicated and from those we consider only 15500 pairs in order to be able to compare the obtained results with the ones from the paper \cite{bogdanova2015detecting}.
-Afterward we have randomly generated the same number of non duplicate pair of posts.
+From this data dump we select only the posts that are questions, the amount of questions is 285651.
+The text of these questions is the training data for generating in-domain word-embeddings through Gensis.
+We, then, extract all question pairs linked as duplicated and we assign them a positive label.
+Since we want to test the performances of our model against the ones obtained by Bogdanova et al., we keep the same dataset size: therefore we consider only 15500 pairs.
+Finally, we randomly generate the same number of non-duplicated pair of questions (negative samples).
 \\
-For our experiments, we divide the dataset in the same way of the paper \cite{bogdanova2015detecting}: 24K pairs for the training set, 6K pairs for the test set and 1K pairs for the validation set.
+The final dataset contains 30K samples and it is perfectly balanced.
+For our experiments, we divide the data as done in \cite{bogdanova2015detecting}: 24K pairs for the training set, 6K pairs for the test set and 1K pairs for the validation set.
 
@@
 Tokenization is the process of breaking up a given text, in this case every question, into units called tokens.
-The tokens may be words or number or punctuation mark: we decide to consider only words and to disregard those tokens that are punctuation, articles and prepositions.
-For each word we took only its lemma.
-Lemmatization is a morphological analysis of words, aiming to remove inflectional forms and to return the base or dictionary form of a word, which is known as the lemma.
+The tokens may be words or number or punctuation mark: in this work, we consider only words discarding those tokens that are punctuation, articles and prepositions.
+For each word we took only its \emph{lemma}.
+Lemmatization is a morphological analysis of words, aiming to remove inflectional forms and to return the base or dictionary form of a word, which is known as the \emph{lemma}.
 
-Then we noticed that some patterns are very frequent but not so relevant in their different forms. Therefore we had some other precautions:
+Moreover, we notice that some patterns are very frequent in our text data but not so relevant in their different forms. Therefore we take some other precautions:
 \begin{itemize}
@@
 \paragraph{Experiments setup.}
-First of all we have trained the model with pretrained English Wikipedia's embeddings \footnote{\url{http://nlp.stanford.edu/data/glove.6B.zip}}.
-In our model we have identified the following hyperparameters:
+First of all we train the model with pre-trained English Wikipedia's embeddings \footnote{\url{http://nlp.stanford.edu/data/glove.6B.zip}}. In our model we identify the following hyper-parameters: 
 \begin{itemize}
-	\item $cl_{u}$, that is the number of units of the one-dimensional convolutional layer
+	\item $cl_{u}$, that is the number of units of the 1-dimensional convolutional layer
 	\item $k$, that is the number of successive words within a window
 \end{itemize}
-Since the hyperparameters are continuous and the hyperparameter space can be very huge, we decide to use a Gaussian Process to approximate the validation accuracy function.
-At each iteration of this process we sample the hyperparameters from Gaussian prior, we train the model with this configuration and we update the Gaussian prior with the validation accuracy of the trained model.
-Moreover we use Early Stopping technique in order to avoid overfitting.
+Since the hyper-parameters are continuous and the hyper-parameter space can be very huge, we use a Gaussian Process to approximate the validation accuracy function.
+At each iteration of this process we sample the hyper-parameters values from Gaussian prior, we train the model with this configuration and we update the Gaussian prior with the validation accuracy of the trained model.
+Moreover, we use Early Stopping technique to avoid overfitting.
 \\
@@
 \paragraph{Results and discussion.}
-The experimental results show that the \emph{max} approach provides the best performances.
+For what concers the issue of unequal text length, the experimental results show that the \emph{max} approach provides the best performances.
 This is probably due to the fact that the \emph{mean} approach is very likely to drop important semantic information from the sentence.
@@
 Figure \ref{fig:lens} shows the distribution of the question lengths of our dataset: it is evident that more than 95\% of the questions contains less than 400 words.
-Hence, we decide to drop the remaining 5\% of the questions.\\
-In Figure \ref{fig:wiki} is represented the validation accuracy resulted from different combinations of hyperparameters values.
-For the sake of clarity we show in the figure only the best $cl_{u}$ value for each window size, but we observe that increasing too much the number of units of the convolutional layer, $cl_{u}$, provides worst performances.
-As the figure indicates, smaller window sizes, provides the best performances.\\
+Hence, we drop the remaining 5\% of the questions.\\
+In Figure \ref{fig:wiki}, it is represented the validation accuracy resulted from different combinations of hyper-parameters values.
+For the sake of clarity, it is shown only the best $cl_{u}$ value for each window size.
+We observe that increasing too much the number of units of the convolutional layer, $cl_{u}$, provides worst performances.
+Furthermore, smaller window sizes, provides the best performances.\\
 Figure \ref{fig:embeddings} shows that, the addition of a trainable embedding layer, provides a performance improvement of around 1\%.
-The figure also highlights that (as stated in Table \ref{table:accuracy}) the model trained with in-domain embeddings outperform that trained using Wikipedia's embeddings.\\
+The figure also highlights that (as stated in Table \ref{table:accuracy}) the model trained with in-domain embeddings outperforms that trained using Wikipedia's embeddings.\\
 The best model possible is, therefore, the CNN Multi-Channel initialized using in-domain word embeddings with $cl_u=300$ and $k=2$. It achieves 89\% accuracy on the test set.
@@
 In this paper, we attempts to replicate the Bogdonova et al.
-paper \cite{bogdanova2015detecting} that propose a method for identifying semantically equivalent questions based on a convolutional neural network.
-We solve the problem of unequal text legths by considering the \emph{max} length, which reaches better performance with respect to the mean approach.
+paper \cite{bogdanova2015detecting}.
+They propose a method for identifying semantically equivalent questions based on a convolutional neural network.
+We solve the problem of unequal text lengths by choosing the \emph{max} approach, which reaches better performance with respect to the mean approach.
 We experimentally show that the proposed CNN achieves high accuracy especially when the word embeddings are pre-trained on in-domain data.
-In particular we found out that the CNN Multi-channel model brings a performance improvement of one-percent with respect to the model with only one matrix of word embeddings .
+In particular, we found out that the CNN Multi-channel model brings a performance improvement of one-percent with respect to the model with only one static matrix of word embeddings .
 This model achieves 89\% accuracy on the test set, that is a result very close to the one of our target.\\
-A possible extension of this work could be to use an LSTM approach to solve the problem of unequal text lengths. Moreover, other deeper architectures could be explored.
+A possible extension of this work could be to use an LSTM approach to solve the problem of unequal text lengths. Moreover, other deeper architectures could be investigated.
 

### 2018-07-16 paper/paper_final.tex
review paper

@@
     \paragraph{The training of in-domain word embeddings.}
-    The paper does not provide any information about the model adopted to train in-domain word embeddings.
-Initially, we tried to build our own \emph{word2vec} model \cite{mikolov2013distributed} trained with the same dataset employed to train the main network \footnote{To do so we followed this good tutorial: \url{http://adventuresinmachinelearning.com/word2vec-keras-tutorial/}}.
+    The paper \cite{bogdanova2015detecting} does not provide any information about the model adopted to train in-domain word embeddings.
+Initially, we tried to build our own \emph{word2vec skip-gram} model \cite{mikolov2013distributed} trained with the same dataset employed to train the main network \footnote{To do so we followed this good tutorial: \url{http://adventuresinmachinelearning.com/word2vec-keras-tutorial/}}.
 However, the training of this network turned out to be very slow and the resulting embeddings performed poorly.
@@
 In Subsection 3.1, we describe in detail the architecture of the Neural Network.
-Then, in subsequent subsections, we focus on the decisions we have made about the things left unspecified by Bogdanova et al.
+Then, in subsequent subsections, we focus on the decisions we have made about the aspects left unspecified by Bogdanova et al.
 %-------------------------------------------------------------------------
@@
 In the first step, the CNN transforms words into real valued feature vectors, also known as \emph{word embeddings}.
-Next, a convolutional layer is used to construct two distributed vector representations $\vec{r}_{q1}$ and $\vec{r}_{q2}$, one for each input question.
-Finally, the CNN computes a similarity score between $\vec{r}_{q1}$ and $\vec{r}_{q2}$.
+Next, a convolutional layer is used to construct two distributed vector representations $\vec{r}_{q_1}$ and $\vec{r}_{q_2}$, one for each input question.
+Finally, the CNN computes a similarity score between $\vec{r}_{q_1}$ and $\vec{r}_{q_2}$.
 Pairs of questions with similarity above a threshold are considered duplicates.
@@
 In this matrix, the $i$-th row corresponds to the word embedding of the $i$-th word in the vocabulary.
-\end{itemize}•
+\end{itemize}
 The input of this layer is a 1-dimensional vector $\vec{q}=[w_1, w_2, ...
@@
 \subsubsection{The convolution}
-We use a convolutional layer to compute the question-wide distributed vector representations $\vec{r}_{q1}$ and $\vec{r}_{q2}$.
+We use a convolutional layer to compute the question-wide distributed vector representations $\vec{r}_{q_1}$ and $\vec{r}_{q_2}$.
 For each question, the convolutional layer first produces local features around each word in the question.
@@
 $\vec{z}_n = [\vec{r}^{w_n}, ... ,\vec{r}^{w_{n+k-1}}]^T$
-\end{center}•
+\end{center}
 The convolutional layer computes the $j$-th element of the vector $\vec{r}_{q} \in \mathbb{R}^{cl_u}$ as follows: 
@@
 \label{eq:conv}
-\end{equation}•
+\end{equation}
 where $W^1 \in \mathbb{R}^{cl_u \times dk}$ is the weight matrix of the convolutional layer and $f$ is the hyperbolic tangent function.
@@
 \subsubsection{Similarity score}
-Given $\vec{r}_{q1}$ and $\vec{r}_{q2}$, i.e.
+Given $\vec{r}_{q_1}$ and $\vec{r}_{q_2}$, i.e.
 the representations for the input pair of questions $(q_1, q_2)$, the last layer of the CNN computes a similarity score between $q_1$ and $q_2$.
@@
 \begin{center}
-$s(q_1, q_2) = \frac{\vec{r}_{q1}}{\lVert \vec{r}_{q1} \rVert} \cdot \frac{\vec{r}_{q2}}{\lVert \vec{r}_{q2} \rVert}$
-\end{center}•
+$s(q_1, q_2) = \frac{\vec{r}_{q_1}}{\lVert \vec{r}_{q_1} \rVert} \cdot \frac{\vec{r}_{q_2}}{\lVert \vec{r}_{q_2} \rVert}$
+\end{center}
 
@@
 \item Look up embedding vectors for IDs and construct a 2D tensor that are input to subsequent layers.
-\end{itemize}•
+\end{itemize}
 Now, most neural network APIs (such as Keras) are “define-and-run” so we cannot change the dimensions of various matrices and tensors during runtime.
@@
 We use Ask Ubuntu data dump \footnote{ \url{https://archive.org/download/stackexchange}} provided in April 2018, that contains posts from 2010 to March 2018.
-From this data dump we select only the posts that are questions, the amount of questions is 285651.
-The text of these questions is the training data for generating in-domain word-embeddings through Gensis.
+From this data dump we select only the posts that are questions, the amount of questions is $285\,651$.
+The text of these questions is used for training both the Gensim word2vec model and the CNN.
 We, then, extract all question pairs linked as duplicated and we assign them a positive label.
-Since we want to test the performances of our model against the ones obtained by Bogdanova et al., we keep the same dataset size: therefore we consider only 15500 pairs.
+Since we want to test the performances of our model against the ones obtained by Bogdanova et al., we keep the same dataset size: therefore we consider only $15\,500$ pairs.
 Finally, we randomly generate the same number of non-duplicated pair of questions (negative samples).
 \\
-The final dataset contains 30K samples and it is perfectly balanced.
+The final dataset contains 31K samples and it is perfectly balanced.
 For our experiments, we divide the data as done in \cite{bogdanova2015detecting}: 24K pairs for the training set, 6K pairs for the test set and 1K pairs for the validation set.
@@
 
-Moreover, we notice that some patterns are very frequent in our text data but not so relevant in their different forms. Therefore we take some other precautions:
+Moreover, we notice that some patterns are very frequent in our text data but not relevant in their different forms. Therefore we take some other precautions:
 \begin{itemize}
